---
title: "Availability and Quality of anthropometric data in SwissPedGrowth"
author: "Lorenz Leuenberger"
output: html_document
date: "2026-03-23"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

This script is to describe the availability and quality of anthropometric data from hospitals participating in the SwissPedGrowth project.

# Set up

## Software


```{r}

library(here)
library(tidyverse)
library(gtsummary)
library(DataExplorer)
library(plotly)
library(ggsankeyfier)
library(cowplot)
library(confintr)
library(survey)
library(srvyr)

```

Functions to calculate z-scores

```{r}

# function for correct rounding
round2 = function(x, digits=0) {
  posneg = sign(x)
  z = abs(x)*10^digits
  z = z + 0.5 + sqrt(.Machine$double.eps)
  z = trunc(z)
  z = z/10^digits
  z*posneg
}

# function to calculate corrected z-scores as described by the WHO. See computation_who.pdf -----

z_score_calc_corr = function(L,M,S,parameter){
  if(is.na(L)|is.na(M)|is.na(S)|is.na(parameter)|parameter<=0){
    return(NA)
  }
  z_score = ((parameter/M)^L-1)/(S*L)
  if (z_score > 3){
    SD3pos = M*(1+S*L*3)^(1/L)
    SD2pos = M*(1+S*L*2)^(1/L)
    SD23pos = SD3pos - SD2pos
    z_score = 3+((parameter-SD3pos)/SD23pos)
    return(z_score)
  } else if (z_score < -3){
    SD3neg = M*(1+S*L*(-3))^(1/L)
    SD2neg = M*(1+S*L*(-2))^(1/L)
    SD23neg = SD2neg - SD3neg
    z_score = -3+((parameter-SD3neg)/SD23neg)
    return(z_score)
  } else{
    return(z_score)
  }
}

```

## Import data


```{r}

# administrative
load(file = here("data","processed", "SwissPedGrowth_included", "data_participant.RData"))
load(file = here("data", "processed", "SwissPedGrowth_included", "data_case.RData"))
load(file = here("data", "processed", "SwissPedGrowth_included", "data_visit_week.RData"))
load(file = here("data", "processed", "SwissPedGrowth_included", "data_encounter.RData"))

data_participant <- data_participant_included
data_case <- data_case_included
data_visit_week <- data_visit_week_included
data_encounter <- data_encounter_included

rm(data_participant_included, data_case_included, data_visit_week_included, data_encounter_included)

# clinical
load(file = here("data","processed", "SwissPedGrowth_included", "data_diagnoses.RData"))

data_diagnoses <- data_diagnoses_included

rm(data_diagnoses_included)

# anthropometrics
load(file = here("data","processed", "SwissPedGrowth_included", "data_height_original.RData"))
load(file = here("data","processed", "SwissPedGrowth_included", "data_weight_original.RData"))
load(file = here("data","processed", "SwissPedGrowth_included", "data_height_clean.RData"))
load(file = here("data","processed", "SwissPedGrowth_included", "data_weight_clean.RData"))
load(file = here("data","processed", "SwissPedGrowth_included", "data_bmi.RData"))
load(file = here("data","processed", "SwissPedGrowth_included", "data_head.RData"))

data_height_original <- data_height_original_included
data_weight_original <- data_weight_original_included
data_height_clean <- data_height_clean_included
data_weight_clean <- data_weight_clean_included
data_bmi <- data_bmi_included
data_head <- data_head_included

rm(data_height_original_included, data_weight_original_included, data_height_clean_included, data_weight_clean_included, data_bmi_included, data_head_included)

# growth references

interpolated_braegger_height <- read.csv(here("data", "raw", "Interpolated-growth-references", "interpolated_braegger_height.csv"))
interpolated_braegger_weight <- read.csv(here("data", "raw", "Interpolated-growth-references", "interpolated_braegger_weight.csv"))
interpolated_braegger_bmi <- read.csv(here("data", "raw", "Interpolated-growth-references", "interpolated_braegger_bmi.csv"))
braegger_length <- read.csv(here("data", "raw", "Interpolated-growth-references", "braegger_length.csv"))
interpolated_braegger_head_circumference <- read.csv(here("data", "raw", "Interpolated-growth-references", "interpolated_braegger_head_circumference.csv"))


# general population

Genpop_summary_statistics_2017 <- read.csv(here("data", "raw", "General_population", "Summary_statistics_2017.csv"))
Genpop_summary_statistics_2023 <- read.csv(here("data", "raw", "General_population", "Summary_statistics_2023.csv"))
```


# Inclusion criteria for analysis


The SwissPedGrowth inclusion criteria are already applied:

Include participants who
- visited a hospital between 25.12.2016 and 07.01.2024 (adapted period for date shifts) based on Administrative Case AND
- were between 0 to 20 years old at visit based on Administrative Case admission

Exclude participants
- with refused GC
- missing birth date

Include data collected between 25.12.2016 and 07.01.2024 (adapted period for date shifts).


Analysis inclusion criteria
Include SwissPedGrowth participants

Exclude participants and visits (and their data)
- with missing sex or missing type of visit


Visits

```{r}
# visits

data_visit_week <- data_visit_week |> 
  mutate(analysis_inclusion_visit_week = factor(case_when(is.na(sex) ~ "Exclude - missing sex",
                                        is.na(visit_week_type) ~ "Exclude - missing information on visit",
                                        TRUE ~ "Include"),
                                     levels = c("Include", "Exclude - missing sex", "Exclude - missing information on visit")))

data_visit_week |> select(analysis_inclusion_visit_week) |> tbl_summary()


```

Participant

```{r}

data_participant <- data_participant |> 
  left_join(data_visit_week |> group_by(participant_id) |> arrange(analysis_inclusion_visit_week) |> slice(1) |> ungroup() |> select(analysis_inclusion_visit_week, participant_id), by = "participant_id")


data_participant <- data_participant |> 
  mutate(analysis_inclusion_participant = factor(case_when(is.na(sex) ~ "Exclude - missing sex",
                                               analysis_inclusion_visit_week == "Exclude - missing information on visit" ~ "Exclude - missing information on visit",
                                               is.na(analysis_inclusion_visit_week) ~ "Exclude - missing information on visit",
                                               TRUE ~ "Include"),
                                     levels = c("Include", "Exclude - missing sex", "Exclude - missing information on visit")))
  


data_participant |> 
  select(analysis_inclusion_participant) |> 
  tbl_summary()

```

Other data

```{r}

# administrative
data_case <- data_case |> 
  left_join(data_participant |> select(participant_id, analysis_inclusion_participant), by = "participant_id") |> 
  left_join(data_visit_week |> group_by(case_id) |> arrange(analysis_inclusion_visit_week) |> slice(1) |> select(case_id, analysis_inclusion_visit_week), by = "case_id")

data_case |> 
  select(analysis_inclusion_participant, analysis_inclusion_visit_week) |> 
  tbl_summary()


data_encounter <- data_encounter |> 
  left_join(data_participant |> select(participant_id, analysis_inclusion_participant), by = "participant_id") |> 
  left_join(data_visit_week |> select(visit_week_id, analysis_inclusion_visit_week), by = "visit_week_id")

data_encounter |> 
  select(analysis_inclusion_participant, analysis_inclusion_visit_week) |> 
  tbl_summary()

# clinical

data_diagnoses <- data_diagnoses |> 
  left_join(data_participant |> select(participant_id, analysis_inclusion_participant), by = "participant_id") |> 
  left_join(data_visit_week |> select(visit_week_id, analysis_inclusion_visit_week), by = "visit_week_id")

data_diagnoses |> 
  select(analysis_inclusion_participant, analysis_inclusion_visit_week) |> 
  tbl_summary()


# anthropometric

data_height_original <- data_height_original |> 
  left_join(data_participant |> select(participant_id, analysis_inclusion_participant), by = "participant_id") |> 
  left_join(data_visit_week |> select(visit_week_id, analysis_inclusion_visit_week), by = "visit_week_id")

data_height_original |> 
  select(analysis_inclusion_participant, analysis_inclusion_visit_week) |> 
  tbl_summary()

data_height_clean <- data_height_clean |> 
  left_join(data_participant |> select(participant_id, analysis_inclusion_participant), by = "participant_id") |> 
  left_join(data_visit_week |> select(visit_week_id, analysis_inclusion_visit_week), by = "visit_week_id")

data_height_clean |> 
  select(analysis_inclusion_participant, analysis_inclusion_visit_week) |> 
  tbl_summary()


data_weight_original <- data_weight_original |> 
  left_join(data_participant |> select(participant_id, analysis_inclusion_participant), by = "participant_id") |> 
  left_join(data_visit_week |> select(visit_week_id, analysis_inclusion_visit_week), by = "visit_week_id")

data_weight_original |> 
  select(analysis_inclusion_participant, analysis_inclusion_visit_week) |> 
  tbl_summary()

data_weight_clean <- data_weight_clean |> 
  left_join(data_participant |> select(participant_id, analysis_inclusion_participant), by = "participant_id") |> 
  left_join(data_visit_week |> select(visit_week_id, analysis_inclusion_visit_week), by = "visit_week_id")

data_weight_clean |> 
  select(analysis_inclusion_participant, analysis_inclusion_visit_week) |> 
  tbl_summary()

data_head <- data_head |> 
  left_join(data_participant |> select(participant_id, analysis_inclusion_participant), by = "participant_id") |> 
  left_join(data_visit_week |> select(visit_week_id, analysis_inclusion_visit_week), by = "visit_week_id")

data_head |> 
  select(analysis_inclusion_participant, analysis_inclusion_visit_week) |> 
  tbl_summary()


data_bmi <- data_bmi |> 
  left_join(data_participant |> select(participant_id, analysis_inclusion_participant), by = "participant_id") |> 
  left_join(data_visit_week |> select(visit_week_id, analysis_inclusion_visit_week), by = "visit_week_id")

data_bmi |> 
  select(analysis_inclusion_participant, analysis_inclusion_visit_week) |> 
  tbl_summary()

```


Apply inclusion criteria

```{r}

data_visit_week <- data_visit_week |> 
  filter(analysis_inclusion_visit_week == "Include")

data_participant <- data_participant |> 
  filter(analysis_inclusion_participant == "Include" & analysis_inclusion_visit_week == "Include") |> 
  select(-c(analysis_inclusion_participant, analysis_inclusion_visit_week))

data_case <- data_case |> 
  filter(analysis_inclusion_participant == "Include" & analysis_inclusion_visit_week == "Include") |> 
  select(-c(analysis_inclusion_participant, analysis_inclusion_visit_week))

data_diagnoses <- data_diagnoses |> 
  filter(analysis_inclusion_participant == "Include" & analysis_inclusion_visit_week == "Include") |> 
  select(-c(analysis_inclusion_participant, analysis_inclusion_visit_week))

data_height_original <- data_height_original |> 
  filter(analysis_inclusion_participant == "Include" & analysis_inclusion_visit_week == "Include") |> 
  select(-c(analysis_inclusion_participant, analysis_inclusion_visit_week))

data_height_clean <- data_height_clean |> 
  filter(analysis_inclusion_participant == "Include" & analysis_inclusion_visit_week == "Include") |> 
  select(-c(analysis_inclusion_participant, analysis_inclusion_visit_week))

data_weight_original <- data_weight_original |> 
  filter(analysis_inclusion_participant == "Include" & analysis_inclusion_visit_week == "Include") |> 
  select(-c(analysis_inclusion_participant, analysis_inclusion_visit_week))

data_weight_clean <- data_weight_clean |> 
  filter(analysis_inclusion_participant == "Include" & analysis_inclusion_visit_week == "Include") |> 
  select(-c(analysis_inclusion_participant, analysis_inclusion_visit_week))

data_head <- data_head |> 
  filter(analysis_inclusion_participant == "Include" & analysis_inclusion_visit_week == "Include") |> 
  select(-c(analysis_inclusion_participant, analysis_inclusion_visit_week))

data_bmi <- data_bmi |> 
  filter(analysis_inclusion_participant == "Include" & analysis_inclusion_visit_week == "Include") |> 
  select(-c(analysis_inclusion_participant, analysis_inclusion_visit_week))


```

# Data preparation

## Code variables

### Nationality

```{r}

data_participant <- data_participant |> 
  mutate(nationality_group = case_when(nationality == "Switzerland" ~ "Swiss",
                                       nationality == "Germany" ~ "German",
                                       nationality == "Portugal"  ~ "Portuguese",
                                       nationality == "Italy" ~ "Italian",
                                       continent_nationality == "Europe" ~ subcontinent_nationality,
                                       TRUE ~ continent_nationality),
         nationality_group_short = case_when(nationality == "Switzerland" ~ "Swiss",
                                             continent_nationality == "Europe" ~ "European",
                                             is.na(continent_nationality)==FALSE ~ "Non-European",
                                             TRUE ~ NA))

data_visit_week <- data_visit_week |> 
  left_join(data_participant |> select(participant_id, nationality_group, nationality_group_short), by = "participant_id")

data_height_original <- data_height_original |> 
  left_join(data_participant |> select(participant_id, nationality_group, nationality_group_short), by = "participant_id")

data_weight_original <- data_weight_original |> 
  left_join(data_participant |> select(participant_id, nationality_group, nationality_group_short), by = "participant_id")

data_head <- data_head |> 
  left_join(data_participant |> select(participant_id, nationality_group, nationality_group_short), by = "participant_id")

data_bmi <- data_bmi |> 
  left_join(data_participant |> select(participant_id, nationality_group, nationality_group_short), by = "participant_id")

```


### Swiss-SEP

```{r}

data_participant <- data_participant |> 
  mutate(swiss_sep_3_decile = factor(case_when(swiss_sep_3 < 50.09 ~ "1",
                                             swiss_sep_3 < 54.74 ~ "2",
                                             swiss_sep_3 < 58.06 ~ "3",
                                             swiss_sep_3 < 60.90 ~ "4",
                                             swiss_sep_3 < 63.56 ~ "5",
                                             swiss_sep_3 < 66.28 ~ "6",
                                             swiss_sep_3 < 69.21 ~ "7",
                                             swiss_sep_3 < 72.65 ~ "8",
                                             swiss_sep_3 < 77.18 ~ "9",
                                             swiss_sep_3 >= 77.18 ~ "10")),
         swiss_sep_3_quintile = factor(case_when(swiss_sep_3_decile == "1" | swiss_sep_3_decile == "2" ~ "1",
                                                 swiss_sep_3_decile == "3" | swiss_sep_3_decile == "4" ~ "2",
                                                 swiss_sep_3_decile == "5" | swiss_sep_3_decile == "6" ~ "3",
                                                 swiss_sep_3_decile == "7" | swiss_sep_3_decile == "8" ~ "4",
                                                 swiss_sep_3_decile == "9" | swiss_sep_3_decile == "10" ~ "5")))

data_visit_week <- data_visit_week |> 
  left_join(data_participant |> select(participant_id, swiss_sep_3_decile, swiss_sep_3_quintile), by = "participant_id")

data_height_original <- data_height_original |> 
  left_join(data_participant |> select(participant_id, swiss_sep_3_decile, swiss_sep_3_quintile), by = "participant_id")

data_weight_original <- data_weight_original |> 
  left_join(data_participant |> select(participant_id, swiss_sep_3_decile, swiss_sep_3_quintile), by = "participant_id")

data_head <- data_head |> 
  left_join(data_participant |> select(participant_id, swiss_sep_3_decile, swiss_sep_3_quintile), by = "participant_id")
            
data_bmi <- data_bmi |> 
  left_join(data_participant |> select(participant_id, swiss_sep_3_decile, swiss_sep_3_quintile), by = "participant_id")

```

### Age

```{r}

data_participant <- data_participant |> 
  mutate(age_years_SwissPedGrowth_start = as.numeric(difftime(ymd("2017-01-01"), birth_date, units = "days"))/365.25,
         age_years_SwissPedGrowth_end = as.numeric(difftime(ymd("2023-12-31"), birth_date, units = "days"))/365.25)


data_bmi <- data_bmi |> 
  mutate(age_years_bmi = age_days_bmi/365.25)

```


### Age groups

```{r}

data_visit_week <- data_visit_week |> 
  mutate(age_group = case_when(age_years_visit_week_start < 1 ~ "Infancy: <1",
                               age_years_visit_week_start < 6 ~ "Preschool age: 1–5",
                               age_years_visit_week_start < 12 ~ "School age: 6–11",
                               age_years_visit_week_start < 16 ~ "Early adolescence: 12–15",
                               age_years_visit_week_start < 20 ~ "Late adolescence: 16–19",
                               age_years_visit_week_start >= 20 ~ "Adult age: >= 20")) |> 
  mutate(age_group = factor(age_group, levels = c("Infancy: <1", "Preschool age: 1–5", "School age: 6–11", "Early adolescence: 12–15", "Late adolescence: 16–19", "Adult age: >= 20")))

data_height_original <- data_height_original |> 
  mutate(age_group = case_when(age_years_height < 1 ~ "Infancy: <1",
                               age_years_height < 6 ~ "Preschool age: 1–5",
                               age_years_height < 12 ~ "School age: 6–11",
                               age_years_height < 16 ~ "Early adolescence: 12–15",
                               age_years_height < 20 ~ "Late adolescence: 16–19",
                               age_years_height >= 20 ~ "Adult age: >= 20")) |> 
  mutate(age_group = factor(age_group, levels = c("Infancy: <1", "Preschool age: 1–5", "School age: 6–11", "Early adolescence: 12–15", "Late adolescence: 16–19", "Adult age: >= 20")))

data_weight_original <- data_weight_original |> 
  mutate(age_group = case_when(age_years_weight < 1 ~ "Infancy: <1",
                               age_years_weight < 6 ~ "Preschool age: 1–5",
                               age_years_weight < 12 ~ "School age: 6–11",
                               age_years_weight < 16 ~ "Early adolescence: 12–15",
                               age_years_weight < 20 ~ "Late adolescence: 16–19",
                               age_years_weight >= 20 ~ "Adult age: >= 20")) |> 
  mutate(age_group = factor(age_group, levels = c("Infancy: <1", "Preschool age: 1–5", "School age: 6–11", "Early adolescence: 12–15", "Late adolescence: 16–19", "Adult age: >= 20")))

data_head <- data_head |> 
  mutate(age_group = case_when(age_years_circumference < 1 ~ "Infancy: <1",
                               age_years_circumference < 6 ~ "Preschool age: 1–5",
                               age_years_circumference < 12 ~ "School age: 6–11",
                               age_years_circumference < 16 ~ "Early adolescence: 12–15",
                               age_years_circumference < 20 ~ "Late adolescence: 16–19",
                               age_years_circumference >= 20 ~ "Adult age: >= 20")) |> 
  mutate(age_group = factor(age_group, levels = c("Infancy: <1", "Preschool age: 1–5", "School age: 6–11", "Early adolescence: 12–15", "Late adolescence: 16–19", "Adult age: >= 20")))

data_bmi <- data_bmi |> 
  mutate(age_group = case_when(age_years_bmi < 1 ~ "Infancy: <1",
                               age_years_bmi < 6 ~ "Preschool age: 1–5",
                               age_years_bmi < 12 ~ "School age: 6–11",
                               age_years_bmi < 16 ~ "Early adolescence: 12–15",
                               age_years_bmi < 20 ~ "Late adolescence: 16–19",
                               age_years_bmi >= 20 ~ "Adult age: >= 20")) |> 
  mutate(age_group = factor(age_group, levels = c("Infancy: <1", "Preschool age: 1–5", "School age: 6–11", "Early adolescence: 12–15", "Late adolescence: 16–19", "Adult age: >= 20")))


```



### Hospital

Hospital

```{r}

data_participant <- data_participant |> 
  mutate(hospital = case_when(hospital == "CHUV" ~ "Lausanne",
                              hospital == "HUG" ~ "Geneva",
                              hospital == "Insel Gruppe AG" ~ "Bern",
                              hospital == "Universitäts-Kinderspital Zürich - Eleonorenstiftung"  ~ "Zurich",
                              hospital == "University Children Hospital Basel" ~ "Basel",
                              hospital == "Luzerner Kantonsspital AG" ~ "Luzern"))

data_visit_week <- data_visit_week |> 
  mutate(hospital = case_when(hospital == "CHUV" ~ "Lausanne",
                              hospital == "HUG" ~ "Geneva",
                              hospital == "Insel Gruppe AG" ~ "Bern",
                              hospital == "Universitäts-Kinderspital Zürich - Eleonorenstiftung"  ~ "Zurich",
                              hospital == "University Children Hospital Basel" ~ "Basel",
                              hospital == "Luzerner Kantonsspital AG" ~ "Luzern"))

data_diagnoses <- data_diagnoses |> 
  mutate(hospital = case_when(hospital == "CHUV" ~ "Lausanne",
                              hospital == "HUG" ~ "Geneva",
                              hospital == "Insel Gruppe AG" ~ "Bern",
                              hospital == "Universitäts-Kinderspital Zürich - Eleonorenstiftung"  ~ "Zurich",
                              hospital == "University Children Hospital Basel" ~ "Basel",
                              hospital == "Luzerner Kantonsspital AG" ~ "Luzern"))

data_height_original <- data_height_original |> 
  mutate(hospital = case_when(hospital == "CHUV" ~ "Lausanne",
                              hospital == "HUG" ~ "Geneva",
                              hospital == "Insel Gruppe AG" ~ "Bern",
                              hospital == "Universitäts-Kinderspital Zürich - Eleonorenstiftung"  ~ "Zurich",
                              hospital == "University Children Hospital Basel" ~ "Basel",
                              hospital == "Luzerner Kantonsspital AG" ~ "Luzern"))

data_weight_original <- data_weight_original |> 
  mutate(hospital = case_when(hospital == "CHUV" ~ "Lausanne",
                              hospital == "HUG" ~ "Geneva",
                              hospital == "Insel Gruppe AG" ~ "Bern",
                              hospital == "Universitäts-Kinderspital Zürich - Eleonorenstiftung"  ~ "Zurich",
                              hospital == "University Children Hospital Basel" ~ "Basel",
                              hospital == "Luzerner Kantonsspital AG" ~ "Luzern"))

data_head <- data_head |> 
  mutate(hospital = case_when(hospital == "CHUV" ~ "Lausanne",
                              hospital == "HUG" ~ "Geneva",
                              hospital == "Insel Gruppe AG" ~ "Bern",
                              hospital == "Universitäts-Kinderspital Zürich - Eleonorenstiftung"  ~ "Zurich",
                              hospital == "University Children Hospital Basel" ~ "Basel",
                              hospital == "Luzerner Kantonsspital AG" ~ "Luzern"))

data_bmi <- data_bmi |> 
  mutate(hospital = case_when(hospital == "CHUV" ~ "Lausanne",
                              hospital == "HUG" ~ "Geneva",
                              hospital == "Insel Gruppe AG" ~ "Bern",
                              hospital == "Universitäts-Kinderspital Zürich - Eleonorenstiftung"  ~ "Zurich",
                              hospital == "University Children Hospital Basel" ~ "Basel",
                              hospital == "Luzerner Kantonsspital AG" ~ "Luzern"))


data_participant <- data_participant |> 
  mutate(hospital = factor(hospital, levels = c("Basel", "Bern", "Geneva", "Lausanne", "Luzern", "Zurich")))

data_visit_week <- data_visit_week |> 
  mutate(hospital = factor(hospital, levels = c("Basel", "Bern", "Geneva", "Lausanne", "Luzern", "Zurich")))

data_diagnoses <- data_diagnoses |> 
  mutate(hospital = factor(hospital, levels = c("Basel", "Bern", "Geneva", "Lausanne", "Luzern", "Zurich")))

data_height_original <- data_height_original |> 
  mutate(hospital = factor(hospital, levels = c("Basel", "Bern", "Geneva", "Lausanne", "Luzern", "Zurich")))

data_weight_original <- data_weight_original |> 
  mutate(hospital = factor(hospital, levels = c("Basel", "Bern", "Geneva", "Lausanne", "Luzern", "Zurich")))

data_head <- data_head |> 
  mutate(hospital = factor(hospital, levels = c("Basel", "Bern", "Geneva", "Lausanne", "Luzern", "Zurich")))

data_bmi <- data_bmi |> 
  mutate(hospital = factor(hospital, levels = c("Basel", "Bern", "Geneva", "Lausanne", "Luzern", "Zurich")))

```


Hospital coded

```{r}

set.seed(1000)

hospital_code <- data_participant |> 
  select(hospital) |> 
  distinct(hospital) |> 
  slice_sample(prop = 1)

hospital_code <- hospital_code |> 
  mutate(hospital_coded = LETTERS[1:n()])


hospital_code


data_participant <- data_participant |> 
  left_join(hospital_code, by = "hospital")

data_visit_week <- data_visit_week |> 
  left_join(hospital_code, by = "hospital")

data_diagnoses <- data_diagnoses |> 
  left_join(hospital_code, by = "hospital")

data_height_original <- data_height_original |> 
  left_join(hospital_code, by = "hospital")

data_weight_original <- data_weight_original |> 
  left_join(hospital_code, by = "hospital")

data_head <- data_head |> 
  left_join(hospital_code, by = "hospital")

data_bmi <- data_bmi |> 
  left_join(hospital_code, by = "hospital")

```



### Consent

```{r}

data_participant <- data_participant |> 
  mutate(general_consent = case_when(is.na(consent_status) ~ "Unkown",
                                     TRUE ~ consent_status))

data_visit_week <- data_visit_week |> 
  mutate(general_consent = case_when(is.na(consent_status) ~ "Unkown",
                                     TRUE ~ consent_status))

```


### Visits

```{r}

data_visit_week <- data_visit_week |> 
  mutate(visit_week_type = factor(visit_week_type,
                             levels = c("Outpatient visit", "ER visit", "Inpatient stay")))

data_participant <- data_participant |> 
  left_join(data_visit_week |>
              filter(visit_week_type == "Outpatient visit") |>
              count(participant_id) |> rename("number_outpatient_visits" = "n"),
            by = "participant_id") |> 
  left_join(data_visit_week |>
              filter(visit_week_type == "ER visit") |>
              count(participant_id) |> rename("number_ER_visits" = "n"),
            by = "participant_id") |> 
  left_join(data_visit_week |>
              filter(visit_week_type == "Inpatient stay") |>
              count(participant_id) |> rename("number_inpatient_stays" = "n"),
            by = "participant_id") |> 
  mutate(outpatient_visit = factor(case_when(number_outpatient_visits == 1 ~ "One visit",
                                      number_outpatient_visits >= 2 ~ "Multiple visits",
                                      is.na(number_outpatient_visits) ~ "No visit"),
                                   levels = c("No visit", "One visit", "Multiple visits")),
         ER_visit = factor(case_when(number_ER_visits == 1 ~ "One visit",
                                      number_ER_visits >= 2 ~ "Multiple visits",
                                      is.na(number_ER_visits) ~ "No visit"),
                                   levels = c("No visit", "One visit", "Multiple visits")),
         inpatient_stay = factor(case_when(number_inpatient_stays == 1 ~ "One visit",
                                      number_inpatient_stays >= 2 ~ "Multiple visits",
                                      is.na(number_inpatient_stays) ~ "No visit"),
                                   levels = c("No visit", "One visit", "Multiple visits")))
  



```


### Diagnoses affecting growth

Define excluded diagnoses affecting growth

```{r}

icd_excluded_temporarily <- c(
  ## Intestinal infections
  "A00", "A01", "A02", "A03", "A04", "A05", "A06", "A07", "A08", "A09",
  
  ## Certain zoonotic bacterial diseases
  "A20", "A21", "A22", "A23", "A24", "A25", "A26", "A27", "A28",
  
  ## Other bacterial diseases
  "A30", "A31", "A32", "A33", "A34", "A35", "A36", "A37", "A38", "A39", "A40", "A41", "A42", "A43", "A44", "A45", "A46", "A47", "A48", "A49",
  
  ## Rickettsioses
  "A75", "A76", "A77", "A78", "A79",
  
  ## Viral infections of the central nervous system
  "A80", "A81", "A82",   "A83", "A84", "A85", "A86", "A87", "A88", "A89",
    
  ## Arthropod-borne viral fevers and viral haemorrhagic fevers
  "A92", "A93", "A94", "A95", "A96", "A97", "A98", "A99",

  ## Viral hepatitis
  "B15", "B16", "B17", "B18", "B19",
  
  ## Systematic mycoses
  "B37", "B38", "B39",
  "B40", "B41", "B42", "B43", "B44", "B45", "B46",
  
  ## Protozoal diseases
  "B50", "B51", "B52", "B53", "B54", "B55", "B56", "B57", "B58", "B59",
  "B60", "B61", "B62", "B63", "B64", "B65", "B66", "B67", "B68", "B69",
  "B70", "B71", "B72", "B73",
  
  ## Helminthiases
  "B74", "B75", "B76", "B77", "B78", "B79",
  "B80", "B81", "B82", "B83",
  
  ## Acute rheumatic fever
  "I00", "I01", "I02",
  
  ## Acute pericarditis
  "I30",
  
  ## Acute and subacute endocarditis
  "I33",
  
  ## Acute myocarditis
  "I40",
  
  ## Influenza and pneumonia
  "J09",
  "J10", "J11", "J12", "J13", "J14", "J15", "J16", "J17", "J18",
  
  ## Other acute lower respiratory infections
  "J20", "J21", "J22",
  
  ## Appendicitis
  "K35", "K36", "K37",
  
  ## Noninfective enteritis and colitis
  "K50", "K51", "K52",
  
  ## Peritonitis
  "K65",
  
  ## Cholecystitis
  "K81",
  
  ## Acute pancreatitis
  "K85",
  
  ## Intestinal malabsorption
  "K90",
  
  ## Postprocedural disorders of digestive system, not elsewhere classified
  "K91",
  
  ## Staphylococcal scalded skin syndrome
  "L00",
  
  ## Infectious arthropathies
  "M00", "M01", "M02", "M03",
    
  ## Salpingitis and oophoritis, Inflammatory disease of uterus, except cervix
  "N70", "N71"
  
)

icd_excluded_first_18_months <- c(
  
  ## Fetus and newborn affected by maternal factors and by complications of pregnancy, labour and delivery
  "P00", "P01", "P02", "P03", "P04",
  
  ## Slow fetal growth and fetal malnutrition
  "P05",
  
  ## Disorders related to short gestation and low birth weight, not elsewhere classified
  "P06",
  
  ## Respiratory and cardiovascular disorders specific to the perinatal period
  "P20", "P21", "P22", "P23", "P24", "P25", "P26", "P27", "P28", "P29",
  
  ## Infections specific to the perinatal period
  "P35", "P36", "P37", "P38", "P39",
  
  ## Hydrops fetalis due to haemolytic disease
  "P56",
  
  ## Transitory endocrine and metabolic disorders specific to fetus and newborn
  "P70", "P71", "P72", "P73", "P74",
  
  ## Digestive system disorders of fetus and newborn
  "P75", "P76", "P77", "P78"
  
)

icd_excluded_permanently <- c(
  ## Tuberculosis
  "A15", "A16", "A17", "A18", "A19",
  
  ## Syphillis
  "A50", "A51", "A52",
  
  ## Human immunodeficiency virus [HIV] disease
  "B20", "B21", "B22", "B23", "B24",
  
  ## Malignant neoplasms
  "C00", "C01", "C02", "C03", "C04", "C05", "C06", "C07", "C08", "C09",
  "C10", "C11", "C12", "C13", "C14", "C15", "C16", "C17", "C18", "C19",
  "C20", "C21", "C22", "C23", "C24", "C25", "C26", "C27", "C28", "C29",
  "C30", "C31", "C32", "C33", "C34", "C35", "C36", "C37", "C38", "C39",
  "C40", "C41", "C42", "C43", "C44", "C45", "C46", "C47", "C48", "C49",
  "C50", "C51", "C52", "C53", "C54", "C55", "C56", "C57", "C58", "C59",
  "C60", "C61", "C62", "C63", "C64", "C65", "C66", "C67", "C68", "C69",
  "C70", "C71", "C72", "C73", "C74", "C75", "C76", "C77", "C78", "C79",
  "C80", "C81", "C82", "C83", "C84", "C85", "C86", "C87", "C88", "C89",
  "C90", "C91", "C92", "C93", "C94", "C95", "C96", "C97",
  
  ## In situ neoplasms
  "D00", "D01", "D02", "D03", "D04", "D05", "D06", "D07", "D08", "D09",
  
  ## Benign neoplasms of GI tract, Hrmonal systems
  "D10", "D11", "D12", "D13",
  "D27",
  "D29.2",
  "D30", "D33", "D34", "D35",
  
  ## Neoplasms of uncertain or unkown behaviour
  "D37", "D38", "D39",
  "D40", "D41", "D42", "D43", "D44", "D45", "D46", "D47", "D48",
  
  ## Haemolytic anaemias
  "D55", "D56", "D57", "D58", "D59",
  
  ## Aplastic and other anaemias
  "D60", "D61", "D63", "D64",
  
  ## Certain disorders involving the immune mechanism (Di-George and more)
  "D80", "D81", "D82", "D83", "D84", "D85", "D86", "D87", "D88", "D89",
  
  ## Disorders of thyroid gland
  "E00", "E01", "E02", "E03", "E04", "E05", "E06", "E07",
  
  ## Diabetes mellitus
  "E10", "E11", "E12", "E13", "E14",
  
  ## Other disorders of glucose regulation and pancreatic internal secretion
  "E15", "E16",
  
  ## Disorders of other endocrine glands
  "E20", "E21", "E22", "E23", "E24", "E25", "E26", "E27", "E28", "E29",
  "E30", "E31", "E32", "E33", "E34", "E35",
  
  ## Malnutrition
  "E40", "E41", "E42", "E43", "E44", "E45", "E46",
  
  ## Other nutritional deficiencies
  "E50", "E51", "E52", "E53", "E54", "E55", "E56", "E57", "E58", "E59",
  "E60", "E61", "E62", "E63", "E64",
  
  ## Obesity and other hyperalimentation
  "E65", "E66", "E67", "E68",
  
  ## Metabolic disorders
  "E70", "E71", "E72", "E73", "E74", "E75", "E76", "E77", "E78", "E79",
  "E80", "E81", "E82", "E83", "E84", "E85", "E86", "E87", "E88", "E89",
  "E90",
  
  ## Mental and behavioural disorders due to psychoactive substance use
  "F10", "F11", "F12", "F13", "F14", "F15", "F16", "F17", "F18", "F19",
  
  ## Depressive episode
  "F32", "F33",
  
  ## Eating disorders
  "F50",
  
  ## Abuse of non-dependence-producing substances
  "F55",
  
  ## Inflammatory diseases of the central nervous system
  "G00", "G01", "G02", "G03", "G04", "G05", "G06", "G07",
  
  ## Systemic atrophies primarily affecting the central nervous system
  "G10", "G11", "G12", "G13", "G14",
  
  ## Hereditary and idiopathic neuropathy
  "G60",
  
  ## Primary disorders of muscles
  "G71",

  ## Chronic rheumatic heart diseases
  "I05", "I06", "I07", "I08", "I09",
  
  ## Diseases of liver
  "K70", "K71", "K72", "K73", "K74", "K75", "K76", "K77",
  
  ## Systemic connective tissue disorders (glucocorticoid treatment)
  "M30", "M31", "M32", "M33", "M34", "M35", "M36",
  
  ## Other osteopathies
  "M86", "M87", "M88", "M89",
  "M90", 
  
  ## Chondropathies
  "M91", "M92", "M93", "M94",
  
  ## Glomerular diseases
  "N00", "N01", "N02", "N03", "N04", "N05", "N06", "N07", "N08",
  
  ## Renal tubulo-interstitial diseases
  "N10", "N11", "N12", "N13", "N14", "N15", "N16",
  
  ## Renal failure
  "N17", "N18", "N19",
  
  ## Other disorders of kidney and ureter
  "N25", "N26", "N27", "N28", "N29",

  ## Pregnancy
  "O00", "O01", "O02", "O03", "O04", "O05", "O06", "O07", "O08", "O09",
  "O10", "O11", "O12", "O13", "O14", "O15", "O16", "O17", "O18", "O19",
  "O20", "O21", "O22", "O23", "O24", "O25", "O26", "O27", "O28", "O29",
  "O30", "O31", "O32", "O33", "O34", "O35", "O36", "O37", "O38", "O39",
  "O40", "O41", "O42", "O43", "O44", "O45", "O46", "O47", "O48", "O49",
  "O50", "O51", "O52", "O53", "O54", "O55", "O56", "O57", "O58", "O59", 
  "O60", "O61", "O62", "O63", "O64", "O65", "O66", "O67", "O68", "O69",
  "O70", "O71", "O72", "O73", "O74", "O75", "O76", "O77", "O78", "O79",
  "O80", "O81", "O82", "O83", "O84", "O85", "O86", "O87", "O88", "O89",
  "O90", "O91", "O92", "O93", "O94", "O95", "O96", "O97", "O98", "O99",

  
  ## Congenital malformations of the nervous system
  "Q00", "Q01", "Q02", "Q03", "Q04", "Q05", "Q06", "Q07",
  
  ## Congenital malformations of the circulatory system
  "Q20", "Q21", "Q22", "Q23", "Q24", "Q25", "Q26", "Q27", "Q28",
  
  ## Congenital malformations of trachea, lung
  "Q32", "Q33",
  
  ## Other congenital malformations of the digestive system
  "Q38", "Q39",
  "Q40", "Q41", "Q42", "Q43", "Q44", "Q45",
  
  ## Indeterminate sex and pseudohermaphroditism
  "Q56",
  
  ## Congenital malformations of the urinary system
  "Q60", "Q61", "Q62", "Q63", "Q64",
  
  ## Congenital malformations and deformations of the musculoskeletal system
  "Q65", "Q66", "Q67", "Q68", "Q69",
  "Q70", "Q71", "Q72", "Q73", "Q74", "Q75", "Q76", "Q77", "Q78", "Q79",
  
  ## Congenital malformation syndromes
  "Q86", "Q87", "Q88", "Q89",
  
  ## Chromosomal abnormalities, not elsewhere classified
  "Q90", "Q91", "Q92", "Q93", "Q94", "Q95", "Q96", "Q97", "Q98", "Q99",
  
  ## Fracture of neck
  "S12",
  
  ## Fracture of rib(s), sternum and thoracic spine
  "S22",
  
  ## Fracture of femur
  "S72",
  
  ## Traumatic amputation of hip and thigh
  "S78",
  
  ## Fracture of lower leg, including ankle
  "S82",
  
  ## Traumatic amputation of lower leg
  "S88",
  
  ## Fracture of foot, except ankle
  "S92",
  
  ## Traumatic amputation of ankle and foot
  "S98",
  
  ## Amputation of limb(s)
  "Y83.5"
  
)



```

Group diagnoses

```{r}

data_diagnoses <- data_diagnoses |> 
  mutate(diagnosis_affecting_growth = factor(case_when(is.na(diagnosis_icd10_code) & is.na(diagnosis_orpha_code_associated_icd) ~ NA,
                                         grepl(paste(icd_excluded_permanently, collapse = "|"), diagnosis_icd10_code) | grepl(paste(icd_excluded_permanently, collapse = "|"), diagnosis_orpha_code_associated_icd) ~ "Affecting growth permanently",
                                         grepl(paste(icd_excluded_first_18_months, collapse = "|"), diagnosis_icd10_code) | grepl(paste(icd_excluded_first_18_months, collapse = "|"), diagnosis_orpha_code_associated_icd) ~ "Affecting growth temporarily",
                                         grepl(paste(icd_excluded_temporarily, collapse = "|"), diagnosis_icd10_code) | grepl(paste(icd_excluded_temporarily, collapse = "|"), diagnosis_orpha_code_associated_icd) ~ "Affecting growth temporarily",
                                         TRUE ~ "Include"),
                                      levels = c("Include", "Affecting growth permanently", "Affecting growth temporarily")))

```

```{r}

data_visit_week <- data_visit_week |> 
  left_join(data_diagnoses |> select(diagnosis_affecting_growth, visit_week_id) |> group_by(visit_week_id) |> arrange(desc(diagnosis_affecting_growth)) |> slice(1) |> ungroup(), by = "visit_week_id")

```


### Anthro availability

#### by participant

```{r}

data_participant <- data_participant |> 
  left_join(data_height_original |>
              count(participant_id) |> rename("number_height_measurements" = "n"),
            by = "participant_id") |>
  left_join(data_weight_original |>
              count(participant_id) |> rename("number_weight_measurements" = "n"),
            by = "participant_id") |> 
  left_join(data_head |>
              count(participant_id) |> rename("number_head_measurements" = "n"),
            by = "participant_id") |> 
  left_join(data_bmi |>
              count(participant_id) |> rename("number_bmi_measurements" = "n"),
            by = "participant_id") |> 
  mutate(height_measurement = factor(case_when(number_height_measurements  == 1 ~ "1 height",
                                        number_height_measurements > 1 ~ "2+ heights",
                                        is.na(number_height_measurements) ~ "No height"),
                                     levels = c("No height", "1 height", "2+ heights")),
         weight_measurement = factor(case_when(number_weight_measurements  == 1 ~ "1 weight",
                                        number_weight_measurements > 1 ~ "2+ weights",
                                        is.na(number_weight_measurements) ~ "No weight"),
                                     levels = c("No weight", "1 weight", "2+ weights")),
         head_measurement = factor(case_when(number_head_measurements  == 1 ~ "1 head circumference",
                                        number_head_measurements > 1 ~ "2+ head circumferences",
                                        is.na(number_head_measurements) ~ "No head circumference"),
                                   levels = c("No head circumference", "1 head circumference", "2+ head circumferences")),
         bmi_measurement = factor(case_when(number_bmi_measurements  == 1 ~ "1 bmi",
                                        number_bmi_measurements > 1 ~ "2+ bmis",
                                        is.na(number_bmi_measurements) ~ "No bmi"),
                                  levels = c("No bmi", "1 bmi", "2+ bmis")))



```


#### by hospital visit

```{r}

data_visit_week <- data_visit_week |> 
  left_join(data_height_original |>
              count(visit_week_id) |> rename("number_height_measurements" = "n"),
            by = "visit_week_id") |>
  left_join(data_weight_original |>
              count(visit_week_id) |> rename("number_weight_measurements" = "n"),
            by = "visit_week_id") |> 
  left_join(data_head |>
              count(visit_week_id) |> rename("number_head_measurements" = "n"),
            by = "visit_week_id") |> 
  left_join(data_bmi |>
              count(visit_week_id) |> rename("number_bmi_measurements" = "n"),
            by = "visit_week_id") |> 
  mutate(height_measurement = factor(case_when(number_height_measurements  == 1 ~ "1 height",
                                        number_height_measurements > 1 ~ "2+ heights",
                                        is.na(number_height_measurements) ~ "No height"),
                                     levels = c("No height", "1 height", "2+ heights")),
         weight_measurement = factor(case_when(number_weight_measurements  == 1 ~ "1 weight",
                                        number_weight_measurements > 1 ~ "2+ weights",
                                        is.na(number_weight_measurements) ~ "No weight"),
                                     levels = c("No weight", "1 weight", "2+ weights")),
         head_measurement = factor(case_when(number_head_measurements  == 1 ~ "1 head circumference",
                                        number_head_measurements > 1 ~ "2+ head circumferences",
                                        is.na(number_head_measurements) ~ "No head circumference"),
                                   levels = c("No head circumference", "1 head circumference", "2+ head circumferences")),
         bmi_measurement = factor(case_when(number_bmi_measurements  == 1 ~ "1 bmi",
                                        number_bmi_measurements > 1 ~ "2+ bmis",
                                        is.na(number_bmi_measurements) ~ "No bmi"),
                                  levels = c("No bmi", "1 bmi", "2+ bmis")))

```


### Anthro quality

Self-developed results: based on self-developed algorithm

Growthcleanr results

Combined results: Self-developed + growth cleanr combined

#### Height

```{r}

### Manual result

data_height_original <- data_height_original |> 
  mutate(manual_result_fct = factor(case_when(manual_result == "Include" ~ "Include - No error",
                                              manual_result == "Swapped-Recoding-Include-as-Weight" ~ "Include - Swapped-Recoding-Include-as-Weight",
                                          manual_result == "Unit-Error-High" | manual_result == "Unit-Error-Low" ~ "Include - Corrected unit error",
                                          manual_result == "Decimal-Error-Low" | manual_result == "Decimal-Error-High" ~ "Include - Corrected decimal point error",
                                          manual_result == "Carried-Forward" ~ "Duplicate - Carried forward",
                                          manual_result == "Same-Day" ~ "Duplicate - Same day",
                                          manual_result == "Exclude - Z-Score" ~ "Exclude - Z-score",
                                          manual_result == "Zero-or-negative-height" ~ "Missing - Zero or negative recording",
                                          manual_result == "Negative-age" ~ "Missing - Negative age"),
                                levels = c("Include - No error", "Include - Swapped-Recoding-Include-as-Weight", "Include - Corrected unit error", "Include - Corrected decimal point error", "Duplicate - Carried forward", "Duplicate - Same day", "Exclude - Z-score", "Missing - Zero or negative recording", "Missing - Negative age")))

data_height_original |> 
  select(manual_result_fct) |> 
  tbl_summary()


### Growthcleanr

data_height_original <- data_height_original |> 
  mutate(growthcleanr_result_fct = factor(case_when(growthcleanr_result == "Include" ~ "Include - No error",
                                              growthcleanr_result == "Swapped-Measurements" ~ "Include - Corrected swapped measurements",
                                              growthcleanr_result == "Carried-Forward" ~ "Duplicate - Carried forward",
                                              growthcleanr_result == "Same-Day" ~ "Duplicate - Same day",
                                              growthcleanr_result == "Longitudinal-Outlier" ~ "Exclude - Longitudinal outlier",
                                              growthcleanr_result == "Single-Outlier" | growthcleanr_result == "Exclude - Extreme-Outlier" ~ "Exclude - Single outlier",
                                              growthcleanr_result == "Missing" ~ "Missing"),
                                levels = c("Include - No error", "Include - Corrected swapped measurements", "Duplicate - Carried forward", "Duplicate - Same day", "Exclude - Longitudinal outlier", "Exclude - Single outlier", "Missing")))

data_height_original |> 
  select(growthcleanr_result_fct) |> 
  tbl_summary()


### Combined

data_height_original <- data_height_original |> 
  mutate(combined_result_fct = factor(combined_result,
                                      levels = c("Include - No-Error", "Include - Corrected-Unit-Error", "Include - Corrected-Decimal-Error", "Include - Swapped-Recoding-Include-as-Weight", "Carried-Forward", "Same-Day", "Exclude - Longitudinal-Outlier", "Exclude - Single-Outlier", "Exclude - Z-Score", "Missing - Recording", "Missing - Age")))

data_height_original |> 
  select(combined_result_fct) |> 
  tbl_summary()


```

#### Weight

```{r}

### Manual result

data_weight_original <- data_weight_original |> 
  mutate(manual_result_fct = factor(case_when(manual_result == "Include" ~ "Include - No error",
                                              manual_result == "Swapped-Recoding-Include-as-Height" ~ "Include - Swapped-Recoding-Include-as-Height",
                                          manual_result == "Unit-Error-High" | manual_result == "Unit-Error-Low" ~ "Include - Corrected unit error",
                                          manual_result == "Decimal-Error-Low1" | manual_result == "Decimal-Error-Low2" | manual_result == "Decimal-Error-High1" | manual_result == "Decimal-Error-High2" ~ "Include - Corrected decimal point error",
                                          manual_result == "Carried-Forward" ~ "Duplicate - Carried forward",
                                          manual_result == "Same-Day" ~ "Duplicate - Same day",
                                          manual_result == "Exclude - Z-Score" ~ "Exclude - Z-score",
                                          manual_result == "Zero-or-negative-weight" ~ "Missing - Zero or negative recording",
                                          manual_result == "Negative-age" ~ "Missing - Negative age"),
                                levels = c("Include - No error", "Include - Swapped-Recoding-Include-as-Height", "Include - Corrected unit error", "Include - Corrected decimal point error", "Duplicate - Carried forward", "Duplicate - Same day", "Exclude - Z-score", "Missing - Zero or negative recording", "Missing - Negative age")))

data_weight_original |> 
  select(manual_result_fct) |> 
  tbl_summary()


### Growthcleanr

data_weight_original <- data_weight_original |> 
  mutate(growthcleanr_result_fct = factor(case_when(growthcleanr_result == "Include" ~ "Include - No error",
                                              growthcleanr_result == "Swapped-Measurements" ~ "Include - Corrected swapped measurements",
                                              growthcleanr_result == "Carried-Forward" ~ "Duplicate - Carried forward",
                                              growthcleanr_result == "Same-Day" ~ "Duplicate - Same day",
                                              growthcleanr_result == "Longitudinal-Outlier" ~ "Exclude - Longitudinal outlier",
                                              growthcleanr_result == "Single-Outlier" | growthcleanr_result == "Exclude - Extreme-Outlier" ~ "Exclude - Single outlier",
                                              growthcleanr_result == "Missing" ~ "Missing"),
                                levels = c("Include - No error", "Include - Corrected swapped measurements", "Duplicate - Carried forward", "Duplicate - Same day", "Exclude - Longitudinal outlier", "Exclude - Single outlier", "Missing")))

data_weight_original |> 
  select(growthcleanr_result_fct) |> 
  tbl_summary()


### Combined

data_weight_original <- data_weight_original |> 
  mutate(combined_result_fct = factor(combined_result,
                                      levels = c("Include - No-Error", "Include - Corrected-Unit-Error", "Include - Corrected-Decimal-Error", "Include - Swapped-Recoding-Include-as-Height", "Carried-Forward", "Same-Day", "Exclude - Longitudinal-Outlier", "Exclude - Single-Outlier", "Exclude - Z-Score", "Missing - Recording", "Missing - Age")))

data_weight_original |> 
  select(combined_result_fct) |> 
  tbl_summary()


```

#### Head circumference

```{r}


data_head <- data_head |> 
  mutate(manual_result_fct = factor(case_when(manual_result == "Include" ~ "Include - No error",
                                          manual_result == "Unit-Error-High" | manual_result == "Unit-Error-Low" ~ "Include - Corrected unit error",
                                          manual_result == "Decimal-Error-Low" | manual_result == "Decimal-Error-High" ~ "Include - Corrected decimal point error",
                                          manual_result == "Carried-Forward" ~ "Duplicate - Carried forward",
                                          manual_result == "Same-Day" ~ "Duplicate - Same day",
                                          manual_result == "Exclude - Z-Score" ~ "Exclude - Z-score",
                                          manual_result == "Zero-or-negative-circumference" ~ "Missing - Zero or negative recording",
                                          manual_result == "Negative-age" ~ "Missing - Negative age"),
                                levels = c("Include - No error", "Include - Corrected unit error", "Include - Corrected decimal point error", "Duplicate - Carried forward", "Duplicate - Same day", "Exclude - Z-score", "Missing - Zero or negative recording", "Missing - Negative age")))

data_head |> 
  select(manual_result_fct) |> 
  tbl_summary()

```

#### BMI

```{r}

data_bmi <- data_bmi |> 
  mutate(combined_result_fct = factor(case_when(combined_result_weight == "Missing - Recording" | combined_result_height == "Missing - Recording" ~ "Missing - Recording",
                                                combined_result_weight == "Missing - Age" | combined_result_height == "Missing - Age" ~ "Missing - Age",
                                                combined_result_weight == "Exclude - Longitudinal-Outlier" | combined_result_height == "Exclude - Longitudinal-Outlier" ~ "Exclude - Longitudinal-Outlier",
                                                combined_result_weight == "Exclude - Single-Outlier" | combined_result_height == "Exclude - Single-Outlier" ~ "Exclude - Single-Outlier",
                                                combined_result_weight == "Exclude - Z-Score" | combined_result_height == "Exclude - Z-Score" ~ "Exclude - Z-Score height or weight",
                                                z_bmi_braegger < (-5) | z_bmi_braegger > 8 ~ "Exclude - Z-Score BMI",
                                                combined_result_weight == "Carried-Forward" | combined_result_height == "Carried-Forward" ~ "Carried-Forward",
                                                combined_result_weight == "Same-Day" | combined_result_height == "Same-Day" ~ "Same-Day",
                                                combined_result_weight == "Include - Swapped-Recoding-Include-as-Weight" | combined_result_height == "Include - Swapped-Recoding-Include-as-Height" ~ "Include - Corrected-Swapped-Recording",
                                                combined_result_weight == "Include - Corrected-Unit-Error" | combined_result_height == "Include - Corrected-Unit-Error" ~ "Include - Corrected-Unit-Error",
                                                combined_result_weight == "Include - Corrected-Decimal-Error" | combined_result_height == "Include - Corrected-Decimal-Error" ~ "Include - Corrected-Decimal-Error",
                                                combined_result_weight == "Include - No-Error" | combined_result_height == "Include - No-Error" ~ "Include - No-Error"),
                                      levels = c("Include - No-Error", "Include - Corrected-Unit-Error", "Include - Corrected-Decimal-Error", "Include - Corrected-Swapped-Recording", "Carried-Forward", "Same-Day", "Exclude - Longitudinal-Outlier", "Exclude - Single-Outlier", "Exclude - Z-Score height or weight", "Exclude - Z-Score BMI", "Missing - Recording", "Missing - Age")))

data_bmi |> 
  select(combined_result_fct) |> 
  tbl_summary()

```

# Descriptive

## Descriptive data check

```{r}

data_participant |> plot_histogram()

data_participant |> plot_bar()

```

Visit data

```{r}

data_visit_week |> select(visit_week_type, visit_week_start_datetime, visit_week_end_datetime, age_years_visit_week_start, age_group) |>  plot_histogram()
data_visit_week |> select(visit_week_type, visit_week_start_datetime, visit_week_end_datetime, age_years_visit_week_start, age_group) |>  plot_bar()

```



Diagnosis data

```{r}

data_diagnoses |> plot_histogram()
data_diagnoses |> plot_bar()

```

Anthro data

```{r}

data_height_original |> plot_histogram()
data_height_original |> plot_bar()

```

```{r}

data_weight_original |> plot_histogram()
data_weight_original |> plot_bar()

```



## Administrative

Number of participants from each hub

```{r}

data_participant |> 
  select(hospital_coded) |> 
  tbl_summary()

```



```{r}

data_participant |> 
  select(sex, nationality_group, nationality_group_short, swiss_sep_3, swiss_sep_3_quintile, hospital_coded, general_consent, number_outpatient_visits, number_ER_visits, number_inpatient_stays) |>
  mutate(number_outpatient_visits = case_when(is.na(number_outpatient_visits) ~ 0,
                                              TRUE ~ number_outpatient_visits),
         number_ER_visits = case_when(is.na(number_ER_visits) ~ 0,
                                              TRUE ~ number_ER_visits),
         number_inpatient_stays = case_when(is.na(number_inpatient_stays) ~ 0,
                                              TRUE ~ number_inpatient_stays)) |> 
  tbl_summary(type = list(c("number_ER_visits", "number_outpatient_visits", "number_inpatient_stays") ~ "continuous2",
                          all_continuous() ~ "continuous2"),
              statistic = all_continuous2() ~ c("{median} ({p25}, {p75})", "{min}, {max}"),
              missing = "ifany",
              missing_stat = "{N_miss} ({p_miss}%)",
              percent = "column",
              digits = all_categorical() ~ 0)

```




## Clinical


Diagnoses

```{r}

data_diagnoses |> 
  select(age_years_diagnosis, diagnosis_affecting_growth) |> 
  tbl_summary()

data_diagnoses |>
  select(age_years_diagnosis) |> 
  plot_histogram()

```

## Anthropometric

Body Height

```{r}

data_height_original |> 
  select(hospital_coded, height_cm, height_datetime, age_years_height) |> 
  tbl_summary(by = "hospital_coded",
              missing = "ifany",
              missing_stat = "{N_miss} ({p_miss}%)") |> 
  add_overall()

data_height_original |> 
  select(height_cm, height_datetime, age_years_height) |> 
  mutate(height_datetime = year(height_datetime)) |> 
  plot_histogram()

data_height_original_SwissPedGrowth |> 
  select(hospital_coded, height_cm, height_datetime, age_years_height) |> 
  tbl_summary(by = "hospital_coded",
              missing = "ifany",
              missing_stat = "{N_miss} ({p_miss}%)") |> 
  add_overall()

data_height_original_SwissPedGrowth |> 
  select(height_cm, height_datetime, age_years_height) |> 
  mutate(height_datetime = year(height_datetime)) |> 
  plot_histogram()

```


Body Weight

```{r}

data_weight_original |> 
  select(hospital_coded, weight_kg, weight_datetime, age_years_weight) |> 
  tbl_summary(by = "hospital_coded",
              missing = "ifany",
              missing_stat = "{N_miss} ({p_miss}%)") |> 
  add_overall()

data_weight_original |> 
  select(weight_kg, weight_datetime, age_years_weight) |> 
  mutate(weight_datetime = year(weight_datetime)) |> 
  plot_histogram()

data_weight_original_SwissPedGrowth |> 
  select(hospital_coded, weight_kg, weight_datetime, age_years_weight) |> 
  tbl_summary(by = "hospital_coded",
              missing = "ifany",
              missing_stat = "{N_miss} ({p_miss}%)") |> 
  add_overall()

data_weight_original_SwissPedGrowth |> 
  select(weight_kg, weight_datetime, age_years_weight) |> 
  mutate(weight_datetime = year(weight_datetime)) |> 
  plot_histogram()

```

Body Mass Index

```{r}

data_bmi |> 
  select(hospital_coded, bmi, bmi_datetime, age_years_bmi) |> 
  tbl_summary(by = "hospital_coded",
              missing = "ifany",
              missing_stat = "{N_miss} ({p_miss}%)") |> 
  add_overall()

data_bmi |> 
  select(bmi, bmi_datetime, age_years_bmi) |> 
  mutate(bmi_datetime = years(bmi_datetime)) |> 
  plot_histogram()


data_bmi_SwissPedGrowth |> 
  select(hospital_coded, bmi, bmi_datetime, age_years_bmi) |> 
  tbl_summary(by = "hospital_coded",
              missing = "ifany",
              missing_stat = "{N_miss} ({p_miss}%)") |> 
  add_overall()

data_bmi_SwissPedGrowth |> 
  select(bmi, bmi_datetime, age_years_bmi) |> 
  mutate(bmi_datetime = years(bmi_datetime)) |> 
  plot_histogram()



```

# Main analysis

## Table 1: Participant's characteristics

```{r}

data_participant |> select(swiss_sep_3) |> plot_histogram()

data_participant |> 
  select(sex, nationality_group_short, swiss_sep_3, swiss_sep_3_quintile, hospital, general_consent, ER_visit, number_ER_visits, outpatient_visit, number_outpatient_visits, inpatient_stay, number_inpatient_stays, age_years_SwissPedGrowth_start) |>
  tbl_summary(type = list(c("number_ER_visits", "number_outpatient_visits", "number_inpatient_stays") ~ "continuous2",
                          all_continuous() ~ "continuous2"),
              statistic = all_continuous2() ~ c("{mean} ({sd})", "{median} ({p25}, {p75})", "{min}, {max}"),
              missing = "ifany",
              missing_stat = "{N_miss} ({p_miss}%)",
              percent = "column",
              digits = list(all_categorical() ~ 0,
                            all_continuous() ~ 1))

```



### eTable: Nationalities

```{r}

nationality_table <- data_participant |> 
  count(nationality) |> 
  filter(is.na(nationality)==FALSE) |> 
  mutate(total = sum(n),
         percent = n/total*100)

nationality_table |> arrange(desc(n)) |>  filter(n >= 900)

```

## Representativeness of general population

### eTable: 2017 Comparison of SwissPedGrowth population with general population

Summary statistics before weighting

```{r}

data_participant_2017 <- data_participant |> 
  left_join(data_visit_week |> mutate(visit_week_year = year(visit_week_start_datetime)) |>  filter(visit_week_year == 2017) |> group_by(participant_id) |> slice(1) |> select(participant_id, visit_week_year), by = "participant_id") |> 
  filter(!is.na(visit_week_year))

data_participant_2017 <- data_participant_2017 |> 
  mutate(age_2017 = floor(as.numeric(difftime(ymd("2017-12-31"), birth_date, units = "days"))/365.25)) |> 
  mutate(age_group_2017 = case_when(age_2017 < 1 ~ "Infancy: <1",
                               age_2017 < 6 ~ "Preschool age: 1–5",
                               age_2017 < 12 ~ "School age: 6–11",
                               age_2017 < 16 ~ "Early adolescence: 12–15",
                               age_2017 >= 16 ~ "Late adolescence: 16–19")) |> 
  mutate(age_group_2017 = factor(age_group_2017, levels = c("Infancy: <1", "Preschool age: 1–5", "School age: 6–11", "Early adolescence: 12–15", "Late adolescence: 16–19")))


data_participant_2017 |> 
  select(age_2017, age_group_2017, sex, nationality_group_short, swiss_sep_3, swiss_sep_3_quintile) |>
  tbl_summary(type = list(all_continuous() ~ "continuous2"),
              statistic = all_continuous2() ~ c("{mean} ({sd})", "{median} ({p25}, {p75})", "{min}, {max}"),
              missing = "ifany",
              missing_stat = "{N_miss} ({p_miss}%)",
              percent = "column",
              digits = list(all_categorical() ~ 0,
                            all_continuous() ~ 1))

Genpop_summary_statistics_2017 |>  
  mutate(percentage = n/total*100)





```

Standardized difference before weighting

```{r}

Genpop_summary_statistics_2017 <- Genpop_summary_statistics_2017 |> 
  select(-c(Mean, SD)) |> 
  filter(Group != "Mean (SD)") |> 
  rename("n_genpop" = "n", "total_genpop" = "total") |> 
  mutate(proportion_genpop = n_genpop/total_genpop)



table_participant_2017 <- data_participant_2017 |> 
  select(age_2017, age_group_2017, sex, nationality_group_short, swiss_sep_3, swiss_sep_3_quintile) |>
  tbl_summary(type = list(all_continuous() ~ "continuous2"),
              statistic = all_continuous2() ~ c("{median} ({p25}, {p75})", "{min}, {max}"),
              missing = "ifany",
              missing_stat = "{N_miss} ({p_miss}%)",
              percent = "column",
              digits = all_categorical() ~ 5)


table_participant_2017 <- table_participant_2017 |> 
  as_tibble() |> 
  rename("Group" = "**Characteristic**", "output" = "**N = 100,752**") |> 
  mutate(Group = case_when(Group == "Infancy: <1" ~ "Infancy: <1",
                           Group == "Preschool age: 1–5" ~ "Preschool age: 1–5",
                           Group == "School age: 6–11" ~ "School age: 6–11",
                           Group == "Early adolescence: 12–15" ~ "Early adolescence: 12–15",
                           Group == "Late adolescence: 16–19" ~ "Late adolescence: 16–19",
                           Group == "Male" ~ "Male",
                           Group == "Female" ~ "Female",
                           Group == "Swiss" ~ "Swiss",
                           Group == "European" ~ "European",
                           Group == "Non-European" ~ "Non-European",
                           Group == "1" ~ "Quntile 1",
                           Group == "2" ~ "Quntile 2",
                           Group == "3" ~ "Quntile 3",
                           Group == "4" ~ "Quntile 4",
                           Group == "5" ~ "Quntile 5")) |> 
  filter(!is.na(Group))


table_participant_2017 <- table_participant_2017 |> 
  separate(
    col = output, 
    into = c("n", "proportion"), 
    sep = " \\("
  ) |> 
  mutate(
    n = str_remove_all(n, ","),
    proportion = str_remove_all(proportion, "[%\\)]")
  ) |> 
  mutate(
    n = as.numeric(n),
    proportion = as.numeric(proportion)
  ) |> 
  mutate(proportion = as.numeric(proportion)/100)

table_participant_2017 <- table_participant_2017 |> 
  rename("n_SwissPedGrowth" = "n", "proportion_SwissPedGrowth" = "proportion")


standardized_difference_table <- Genpop_summary_statistics_2017 |>
  left_join(table_participant_2017, by = "Group")


standardized_difference_table <- standardized_difference_table |> 
  mutate(SPD = 2*(asin(sqrt(proportion_SwissPedGrowth)) - asin(sqrt(proportion_genpop))))

standardized_difference_table |> select(Group, proportion_SwissPedGrowth, proportion_genpop, SPD)

```


Weighting using raking and survey package


```{r}

# target margins of the genpop

pop.age <- Genpop_summary_statistics_2017 |> 
  filter(Variable == "Age") |> 
  mutate(age = factor(Group,
                      levels = c("Infancy: <1", "Preschool age: 1–5", "School age: 6–11", "Early adolescence: 12–15", "Late adolescence: 16–19"))) |> 
  mutate(Freq = proportion_genpop) |> 
  select(age, Freq)
  
pop.sex <- Genpop_summary_statistics_2017 |> 
  filter(Variable == "Sex") |> 
  mutate(sex = factor(Group,
                      levels = c("Female", "Male"))) |> 
  mutate(Freq = proportion_genpop) |> 
  select(sex, Freq)

pop.nationality <- Genpop_summary_statistics_2017 |> 
  filter(Variable == "Nationality") |> 
  filter(Group != "Missing") |> 
  mutate(nationality = factor(Group,
                      levels = c("Swiss", "European", "Non-European"))) |> 
  mutate(Freq = proportion_genpop) |> 
  select(nationality, Freq)


pop.ssep <- Genpop_summary_statistics_2017 |> 
  filter(Variable == "SSEP") |> 
  mutate(swiss_sep_3_quintile = factor(Group,
                                     levels = c("Quntile 1", "Quntile 2","Quntile 3","Quntile 4","Quntile 5"),
                                     labels = c("1", "2", "3", "4", "5"))) |> 
  mutate(Freq = proportion_genpop) |> 
  select(swiss_sep_3_quintile, Freq)


data_to_rake_2017 <- data_participant_2017 |> 
  select(participant_id, age_group_2017, sex, nationality_group_short, swiss_sep_3_quintile) |> 
  mutate(age = factor(age_group_2017,
                      levels = c("Infancy: <1", "Preschool age: 1–5", "School age: 6–11", "Early adolescence: 12–15", "Late adolescence: 16–19"),
                      labels = c("Infancy: <1", "Preschool age: 1–5", "School age: 6–11", "Early adolescence: 12–15", "Late adolescence: 16–19")),
         sex = factor(sex,
                      levels = c("Female", "Male")),
         nationality = factor(nationality_group_short,
                              levels = c("Swiss", "European", "Non-European")),
         swiss_sep_3_quintile = factor(swiss_sep_3_quintile,
                                     levels = c("1", "2", "3", "4", "5"))) |> 
  select(participant_id, age, sex, nationality, swiss_sep_3_quintile) |> 
  drop_na()



data_raked_2017 <- rake(svydesign(ids = ~participant_id, data = data_to_rake_2017),
                        sample.margins = list(~age, ~sex, ~nationality, ~swiss_sep_3_quintile),
                        population.margins = list(pop.age, pop.sex, pop.nationality, pop.ssep))

weights_2017 <- data.frame(participant_id = data_to_rake_2017$participant_id,
                           stabilized_weight = weights(data_raked_2017)/mean(weights(data_raked_2017)))

summary(weights_2017$stabilized_weight)


# add weights back to data

data_participant_2017 <- data_participant_2017 |> 
  left_join(weights_2017, by = "participant_id")

```


Summary statistics after weighting

```{r}

svydesign(id = ~1, data = data_participant_2017 |> filter(!is.na(stabilized_weight)), weights = ~stabilized_weight) |> 
  as_survey() |> 
  select(age_2017, age_group_2017, sex, nationality_group_short, swiss_sep_3, swiss_sep_3_quintile) |>
  tbl_svysummary(type = list(all_continuous() ~ "continuous2"),
              statistic = list(all_continuous2() ~ c("{mean} ({sd})", "{median} ({p25}, {p75})", "{min}, {max}"),
                               all_categorical() ~ c("{n_unweighted} ({p})")),
              missing = "ifany",
              missing_stat = "{N_miss} ({p_miss}%)",
              percent = "column",
              digits = list(all_categorical() ~ 0,
                            all_continuous() ~ 1))


```


Standardized difference after weighting

```{r}

table_participant_2017 <- svydesign(id = ~1, data = data_participant_2017 |> filter(!is.na(stabilized_weight)), weights = ~stabilized_weight) |> 
  as_survey() |> 
  select(age_group_2017, sex, nationality_group_short, swiss_sep_3_quintile) |>
  tbl_svysummary(type = list(all_continuous() ~ "continuous2"),
              statistic = list(all_continuous2() ~ c("{mean} ({sd})", "{median} ({p25}, {p75})", "{min}, {max}"),
                               all_categorical() ~ c("{n_unweighted} ({p})")),
              missing = "ifany",
              missing_stat = "{N_miss} ({p_miss}%)",
              percent = "column",
              digits = list(all_categorical() ~ 5,
                            all_continuous() ~ 1))


table_participant_2017 <- table_participant_2017 |> 
  as_tibble() |> 
  rename("Group" = "**Characteristic**", "output" = "**N = 85,750**") |> 
  mutate(Group = case_when(Group == "Infancy: <1" ~ "Infancy: <1",
                           Group == "Preschool age: 1–5" ~ "Preschool age: 1–5",
                           Group == "School age: 6–11" ~ "School age: 6–11",
                           Group == "Early adolescence: 12–15" ~ "Early adolescence: 12–15",
                           Group == "Late adolescence: 16–19" ~ "Late adolescence: 16–19",
                           Group == "Male" ~ "Male",
                           Group == "Female" ~ "Female",
                           Group == "Swiss" ~ "Swiss",
                           Group == "European" ~ "European",
                           Group == "Non-European" ~ "Non-European",
                           Group == "Missing" ~ "Missing",
                           Group == "1" ~ "Quntile 1",
                           Group == "2" ~ "Quntile 2",
                           Group == "3" ~ "Quntile 3",
                           Group == "4" ~ "Quntile 4",
                           Group == "5" ~ "Quntile 5")) |> 
  filter(!is.na(Group))


table_participant_2017 <- table_participant_2017 |> 
  separate(
    col = output, 
    into = c("n", "proportion"), 
    sep = " \\("
  ) |> 
  mutate(
    n = str_remove_all(n, ","),
    proportion = str_remove_all(proportion, "[%\\)]")
  ) |> 
  mutate(
    n = as.numeric(n),
    proportion = as.numeric(proportion)
  ) |> 
  mutate(proportion = as.numeric(proportion)/100)

table_participant_2017 <- table_participant_2017 |> 
  rename("n_SwissPedGrowth" = "n", "proportion_SwissPedGrowth" = "proportion")


standardized_difference_table <- Genpop_summary_statistics_2017 |>
  left_join(table_participant_2017, by = "Group")


standardized_difference_table <- standardized_difference_table |> 
  mutate(SPD = 2*(asin(sqrt(proportion_SwissPedGrowth)) - asin(sqrt(proportion_genpop))))

standardized_difference_table |> select(Group, proportion_SwissPedGrowth, proportion_genpop, SPD) |> mutate(across(where(is.numeric), \(x) format(x, scientific = FALSE)))

```






### eTable: 2023 Comparison of SwissPedGrowth population with general population

Summary statistics before weighting

```{r}

data_participant_2023 <- data_participant |> 
  left_join(data_visit_week |> mutate(visit_week_year = year(visit_week_start_datetime)) |>  filter(visit_week_year == 2023) |> group_by(participant_id) |> slice(1) |> select(participant_id, visit_week_year), by = "participant_id") |> 
  filter(!is.na(visit_week_year))

data_participant_2023 <- data_participant_2023 |> 
  mutate(age_2023 = floor(as.numeric(difftime(ymd("2023-12-31"), birth_date, units = "days"))/365.25)) |> 
  mutate(age_group_2023 = case_when(age_2023 < 1 ~ "Infancy: <1",
                               age_2023 < 6 ~ "Preschool age: 1–5",
                               age_2023 < 12 ~ "School age: 6–11",
                               age_2023 < 16 ~ "Early adolescence: 12–15",
                               age_2023 >= 16 ~ "Late adolescence: 16–19")) |> 
  mutate(age_group_2023 = factor(age_group_2023, levels = c("Infancy: <1", "Preschool age: 1–5", "School age: 6–11", "Early adolescence: 12–15", "Late adolescence: 16–19")))


data_participant_2023 |> 
  select(age_2023, age_group_2023, sex, nationality_group_short, swiss_sep_3, swiss_sep_3_quintile) |>
  tbl_summary(type = list(all_continuous() ~ "continuous2"),
              statistic = all_continuous2() ~ c("{mean} ({sd})", "{median} ({p25}, {p75})", "{min}, {max}"),
              missing = "ifany",
              missing_stat = "{N_miss} ({p_miss}%)",
              percent = "column",
              digits = list(all_categorical() ~ 0,
                            all_continuous() ~ 1))

Genpop_summary_statistics_2023 |>  
  mutate(percentage = n/total*100)





```

Standardized difference before weighting

```{r}

Genpop_summary_statistics_2023 <- Genpop_summary_statistics_2023 |> 
  select(-c(Mean, SD)) |> 
  filter(Group != "Mean (SD)") |> 
  rename("n_genpop" = "n", "total_genpop" = "total") |> 
  mutate(proportion_genpop = n_genpop/total_genpop)



table_participant_2023 <- data_participant_2023 |> 
  select(age_2023, age_group_2023, sex, nationality_group_short, swiss_sep_3, swiss_sep_3_quintile) |>
  tbl_summary(type = list(all_continuous() ~ "continuous2"),
              statistic = all_continuous2() ~ c("{median} ({p25}, {p75})", "{min}, {max}"),
              missing = "ifany",
              missing_stat = "{N_miss} ({p_miss}%)",
              percent = "column",
              digits = all_categorical() ~ 5)


table_participant_2023 <- table_participant_2023 |> 
  as_tibble() |> 
  rename("Group" = "**Characteristic**", "output" = "**N = 89,500**") |> 
  mutate(Group = case_when(Group == "Infancy: <1" ~ "Infancy: <1",
                           Group == "Preschool age: 1–5" ~ "Preschool age: 1–5",
                           Group == "School age: 6–11" ~ "School age: 6–11",
                           Group == "Early adolescence: 12–15" ~ "Early adolescence: 12–15",
                           Group == "Late adolescence: 16–19" ~ "Late adolescence: 16–19",
                           Group == "Male" ~ "Male",
                           Group == "Female" ~ "Female",
                           Group == "Swiss" ~ "Swiss",
                           Group == "European" ~ "European",
                           Group == "Non-European" ~ "Non-European",
                           Group == "1" ~ "Quntile 1",
                           Group == "2" ~ "Quntile 2",
                           Group == "3" ~ "Quntile 3",
                           Group == "4" ~ "Quntile 4",
                           Group == "5" ~ "Quntile 5")) |> 
  filter(!is.na(Group))


table_participant_2023 <- table_participant_2023 |> 
  separate(
    col = output, 
    into = c("n", "proportion"), 
    sep = " \\("
  ) |> 
  mutate(
    n = str_remove_all(n, ","),
    proportion = str_remove_all(proportion, "[%\\)]")
  ) |> 
  mutate(
    n = as.numeric(n),
    proportion = as.numeric(proportion)
  ) |> 
  mutate(proportion = as.numeric(proportion)/100)

table_participant_2023 <- table_participant_2023 |> 
  rename("n_SwissPedGrowth" = "n", "proportion_SwissPedGrowth" = "proportion")


standardized_difference_table <- Genpop_summary_statistics_2023 |>
  left_join(table_participant_2023, by = "Group")


standardized_difference_table <- standardized_difference_table |> 
  mutate(SPD = 2*(asin(sqrt(proportion_SwissPedGrowth)) - asin(sqrt(proportion_genpop))))

standardized_difference_table |> select(Group, proportion_SwissPedGrowth, proportion_genpop, SPD)

```


Weighting using raking and survey package


```{r}

# target margins of the genpop

pop.age <- Genpop_summary_statistics_2023 |> 
  filter(Variable == "Age") |> 
  mutate(age = factor(Group,
                      levels = c("Infancy: <1", "Preschool age: 1–5", "School age: 6–11", "Early adolescence: 12–15", "Late adolescence: 16–19"))) |> 
  mutate(Freq = proportion_genpop) |> 
  select(age, Freq)
  
pop.sex <- Genpop_summary_statistics_2023 |> 
  filter(Variable == "Sex") |> 
  mutate(sex = factor(Group,
                      levels = c("Female", "Male"))) |> 
  mutate(Freq = proportion_genpop) |> 
  select(sex, Freq)

pop.nationality <- Genpop_summary_statistics_2023 |> 
  filter(Variable == "Nationality") |> 
  filter(Group != "Missing") |> 
  mutate(nationality = factor(Group,
                      levels = c("Swiss", "European", "Non-European"))) |> 
  mutate(Freq = proportion_genpop) |> 
  select(nationality, Freq)


pop.ssep <- Genpop_summary_statistics_2023 |> 
  filter(Variable == "SSEP") |> 
  mutate(swiss_sep_3_quintile = factor(Group,
                                     levels = c("Quntile 1", "Quntile 2","Quntile 3","Quntile 4","Quntile 5"),
                                     labels = c("1", "2", "3", "4", "5"))) |> 
  mutate(Freq = proportion_genpop) |> 
  select(swiss_sep_3_quintile, Freq)


data_to_rake_2023 <- data_participant_2023 |> 
  select(participant_id, age_group_2023, sex, nationality_group_short, swiss_sep_3_quintile) |> 
  mutate(age = factor(age_group_2023,
                      levels = c("Infancy: <1", "Preschool age: 1–5", "School age: 6–11", "Early adolescence: 12–15", "Late adolescence: 16–19"),
                      labels = c("Infancy: <1", "Preschool age: 1–5", "School age: 6–11", "Early adolescence: 12–15", "Late adolescence: 16–19")),
         sex = factor(sex,
                      levels = c("Female", "Male")),
         nationality = factor(nationality_group_short,
                              levels = c("Swiss", "European", "Non-European")),
         swiss_sep_3_quintile = factor(swiss_sep_3_quintile,
                                     levels = c("1", "2", "3", "4", "5"))) |> 
  select(participant_id, age, sex, nationality, swiss_sep_3_quintile) |> 
  drop_na()



data_raked_2023 <- rake(svydesign(ids = ~participant_id, data = data_to_rake_2023),
                        sample.margins = list(~age, ~sex, ~nationality, ~swiss_sep_3_quintile),
                        population.margins = list(pop.age, pop.sex, pop.nationality, pop.ssep))

weights_2023 <- data.frame(participant_id = data_to_rake_2023$participant_id,
                           stabilized_weight = weights(data_raked_2023)/mean(weights(data_raked_2023)))

summary(weights_2023$stabilized_weight)


# add weights back to data

data_participant_2023 <- data_participant_2023 |> 
  left_join(weights_2023, by = "participant_id")

```


Summary statistics after weighting

```{r}

svydesign(id = ~1, data = data_participant_2023 |> filter(!is.na(stabilized_weight)), weights = ~stabilized_weight) |> 
  as_survey() |> 
  select(age_2023, age_group_2023, sex, nationality_group_short, swiss_sep_3, swiss_sep_3_quintile) |>
  tbl_svysummary(type = list(all_continuous() ~ "continuous2"),
              statistic = list(all_continuous2() ~ c("{mean} ({sd})", "{median} ({p25}, {p75})", "{min}, {max}"),
                               all_categorical() ~ c("{n_unweighted} ({p})")),
              missing = "ifany",
              missing_stat = "{N_miss} ({p_miss}%)",
              percent = "column",
              digits = list(all_categorical() ~ 0,
                            all_continuous() ~ 1))


```


Standardized difference after weighting

```{r}

table_participant_2023 <- svydesign(id = ~1, data = data_participant_2023 |> filter(!is.na(stabilized_weight)), weights = ~stabilized_weight) |> 
  as_survey() |> 
  select(age_group_2023, sex, nationality_group_short, swiss_sep_3_quintile) |>
  tbl_svysummary(type = list(all_continuous() ~ "continuous2"),
              statistic = list(all_continuous2() ~ c("{mean} ({sd})", "{median} ({p25}, {p75})", "{min}, {max}"),
                               all_categorical() ~ c("{n_unweighted} ({p})")),
              missing = "ifany",
              missing_stat = "{N_miss} ({p_miss}%)",
              percent = "column",
              digits = list(all_categorical() ~ 5,
                            all_continuous() ~ 1))


table_participant_2023 <- table_participant_2023 |> 
  as_tibble() |> 
  rename("Group" = "**Characteristic**", "output" = "**N = 82,066**") |> 
  mutate(Group = case_when(Group == "Infancy: <1" ~ "Infancy: <1",
                           Group == "Preschool age: 1–5" ~ "Preschool age: 1–5",
                           Group == "School age: 6–11" ~ "School age: 6–11",
                           Group == "Early adolescence: 12–15" ~ "Early adolescence: 12–15",
                           Group == "Late adolescence: 16–19" ~ "Late adolescence: 16–19",
                           Group == "Male" ~ "Male",
                           Group == "Female" ~ "Female",
                           Group == "Swiss" ~ "Swiss",
                           Group == "European" ~ "European",
                           Group == "Non-European" ~ "Non-European",
                           Group == "Missing" ~ "Missing",
                           Group == "1" ~ "Quntile 1",
                           Group == "2" ~ "Quntile 2",
                           Group == "3" ~ "Quntile 3",
                           Group == "4" ~ "Quntile 4",
                           Group == "5" ~ "Quntile 5")) |> 
  filter(!is.na(Group))


table_participant_2023 <- table_participant_2023 |> 
  separate(
    col = output, 
    into = c("n", "proportion"), 
    sep = " \\("
  ) |> 
  mutate(
    n = str_remove_all(n, ","),
    proportion = str_remove_all(proportion, "[%\\)]")
  ) |> 
  mutate(
    n = as.numeric(n),
    proportion = as.numeric(proportion)
  ) |> 
  mutate(proportion = as.numeric(proportion)/100)

table_participant_2023 <- table_participant_2023 |> 
  rename("n_SwissPedGrowth" = "n", "proportion_SwissPedGrowth" = "proportion")


standardized_difference_table <- Genpop_summary_statistics_2023 |>
  left_join(table_participant_2023, by = "Group")


standardized_difference_table <- standardized_difference_table |> 
  mutate(SPD = 2*(asin(sqrt(proportion_SwissPedGrowth)) - asin(sqrt(proportion_genpop))))

standardized_difference_table |> select(Group, proportion_SwissPedGrowth, proportion_genpop, SPD) |> mutate(across(where(is.numeric), \(x) format(x, scientific = FALSE)))

```






## Table 2: Visit's characteristics

```{r}

data_visit_week |> select(visit_week_type) |> tbl_summary()

data_visit_week |> 
  select(visit_week_type, sex, age_years_visit_week_start, age_group, nationality_group_short, swiss_sep_3, swiss_sep_3_quintile, hospital, general_consent, diagnosis_affecting_growth) |>
  tbl_summary(by = "visit_week_type",
              type = list(all_continuous() ~ "continuous2"),
              statistic = list(all_continuous2() ~ c("{mean} ({sd})", "{median} ({p25}, {p75})", "{min}, {max}"),
                               all_categorical() ~ c("{n} ({p})")),
              missing = "ifany",
              missing_stat = "{N_miss} ({p_miss})",
              percent = "column",
              digits = list(all_categorical() ~ 0,
                            all_continuous() ~ 1)) |> 
  add_overall()

```

Some inpatient visits don't have a diagnosis!

```{r}


data_case |> 
  filter(case_carehandling == "Inpatient care") |> 
  left_join(data_diagnoses |> select(diagnosis_affecting_growth, case_id) |> group_by(case_id) |> slice(1) |> ungroup(), by = "case_id") |> 
  select(hospital, diagnosis_affecting_growth) |> 
  tbl_summary(by = hospital)

```


## Aim 1: Availability

Total number of measurements

```{r}

data_height_original |> 
  select(height_id, hospital_coded) |> 
  mutate(number_measurements = "Height") |> 
  bind_rows(data_weight_original |> select(weight_id, hospital_coded) |> mutate(number_measurements = "Weight")) |> 
  bind_rows(data_bmi |> select(weight_id, hospital_coded) |> mutate(number_measurements = "Body Mass Index")) |>
  bind_rows(data_head |> select(circumference_id, hospital_coded) |> mutate(number_measurements = "Head circumference")) |> 
  select(number_measurements, hospital_coded) |> 
  tbl_summary(by = hospital_coded,
              statistic = everything() ~ "{n}",
              label = list(number_measurements = "Number of recorded values")) |> 
  add_overall()

```

### eTable: Per patient


```{r}
data_participant |> 
  select(height_measurement, number_height_measurements, weight_measurement, number_weight_measurements, head_measurement, number_head_measurements, bmi_measurement, number_bmi_measurements) |> 
  tbl_summary(type = all_continuous() ~ "continuous2",
              statistic = list(all_continuous2() ~ "{median} [{p25}, {p75}]",
                               all_categorical() ~ "{n} ({p})"),
              missing = "ifany",
              missing_stat = "{N_miss} ({p_miss}%)")
```


### eTable: Per hospital visit

```{r}

data_visit_week |>  
  select(visit_week_type, height_measurement, number_height_measurements, weight_measurement, number_weight_measurements, head_measurement, number_head_measurements, bmi_measurement, number_bmi_measurements) |> 
  tbl_summary(by = "visit_week_type",
              type = list(c("number_height_measurements", "number_weight_measurements", "number_head_measurements", "number_bmi_measurements") ~ "continuous2",
                          all_continuous() ~ "continuous2"),
              statistic = list(all_continuous2() ~ "{median} [{p25}, {p75}]",
                               all_categorical() ~ "{n} ({p})"),
              missing = "ifany",
              missing_stat = "{N_miss} ({p_miss}%)") |> 
  add_overall()

```

### eTable: Compare visit characteristis with and without measurement


```{r}

data_visit_week |>
  mutate(height_measurement = case_when(height_measurement == "No height" ~ "No height",
                                                    TRUE ~ "Height available")) |> 
  select(height_measurement) |>
  tbl_summary()

data_visit_week |>
  mutate(height_measurement = case_when(height_measurement == "No height" ~ "No height",
                                                    TRUE ~ "Height available")) |> 
  select(height_measurement, sex, age_years_visit_week_start, age_group, nationality_group_short, swiss_sep_3, swiss_sep_3_quintile, hospital_coded, general_consent, visit_week_type) |>
  tbl_summary(by = "height_measurement",
              type = list(all_continuous() ~ "continuous2"),
              statistic = list(all_continuous2() ~ c("{mean} ({sd})", "{median} ({p25}, {p75})", "{min}, {max}"),
                               all_categorical() ~ "{n} ({p})"),
              missing = "ifany",
              missing_stat = "{N_miss} ({p_miss}%)",
              percent = "row",
              digits = list(all_categorical() ~ 0,
                            all_continuous() ~ 1)) |> 
  add_p(test = list("swiss_sep_3" ~ "t.test",
                    "age_years_visit_week_start" ~ "wilcox.test",
                    all_categorical() ~ "chisq.test")) |> 
  add_overall()

```


```{r}

data_visit_week |>
  mutate(weight_measurement = case_when(weight_measurement == "No weight" ~ "No weight",
                                                    TRUE ~ "weight available")) |> 
  select(weight_measurement) |>
  tbl_summary()

data_visit_week |>
  mutate(weight_measurement = factor(case_when(weight_measurement == "No weight" ~ "No weight",
                                                    TRUE ~ "Weight available"),
                                     levels = c("Weight available", "No weight"))) |> 
  select(weight_measurement, sex, age_years_visit_week_start, age_group, nationality_group_short, swiss_sep_3, swiss_sep_3_quintile, hospital_coded, general_consent, visit_week_type) |>
  tbl_summary(by = "weight_measurement",
              type = list(all_continuous() ~ "continuous2"),
              statistic = list(all_continuous2() ~ c("{mean} ({sd})", "{median} ({p25}, {p75})", "{min}, {max}"),
                               all_categorical() ~ "{n} ({p})"),
              missing = "ifany",
              missing_stat = "{N_miss} ({p_miss}%)",
              percent = "row",
              digits = list(all_categorical() ~ 0,
                            all_continuous() ~ 1)) |> 
  add_p(test = list("swiss_sep_3" ~ "t.test",
                    "age_years_visit_week_start" ~ "wilcox.test",
                    all_categorical() ~ "chisq.test")) |> 
  modify_fmt_fun(
    p.value = function(x) {
      ifelse(
        x < 0.0001, 
        "<0.0001", 
        format(round(x, 4), nsmall = 4))  # Show 4 decimal places
    }
  ) |> 
  add_overall()

```

### Figure 1: Per visit by hospital, by visit type, by age group

Height

```{r}

plot_data <- data_visit_week |>
  mutate(height_measurement = case_when(number_height_measurements >= 1 ~ "yes",
                                                TRUE ~ "no")) |>
  select(hospital_coded, height_measurement, visit_week_type, age_group) |>
  group_by(hospital_coded, visit_week_type, age_group) |>
  count(height_measurement) |>
  ungroup() |>
  pivot_wider(names_from = height_measurement,
              values_from = n,
              values_fill = 0) |>
  mutate(total = yes + no,
         yes_prop = yes / total) |>
  rowwise() |>
  mutate(
    ci = list(prop.test(yes, total)$conf.int),
    ci_lower = ci[1],
    ci_upper = ci[2]
  ) |>
  ungroup() |>
  select(-ci)

plot_height_by_hospital_coded_outpatient <- plot_data |> 
  filter(visit_week_type == "Outpatient visit") |> 
  ggplot(aes(x = hospital_coded, y = yes_prop, fill = age_group)) + 
  geom_col(stat = "identity", position = position_dodge(width = 0.75), width = 0.75)+
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = 0.75), width = 0.5) +
  scale_y_continuous(labels = scales::percent, limits = c(0, 1), breaks = c(0, 0.25, 0.5, 0.75, 1), expand = c(0,0))+
  scale_fill_manual(name = "Age group (years)",
                    values = c("grey80", "grey60", "grey40", "grey20", "grey10"))+
  labs(y = "Visits (%) with height",
       x = "Hospital",
       title = "Outpatient visit")+
  theme_minimal()+
  theme(panel.grid.major.x = element_blank(),
        axis.text = element_text(color = "black", size = 8),
        axis.title = element_text(color = "black", size = 8),
        title = element_text(color = "black", size = 8, face = "bold"))

plot_height_by_hospital_coded_outpatient

plot_height_by_hospital_coded_ER <- plot_data |> 
  filter(visit_week_type == "ER visit") |> 
  ggplot(aes(x = hospital_coded, y = yes_prop, fill = age_group)) + 
  geom_col(stat = "identity", position = position_dodge(width = 0.75), width = 0.75)+
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = 0.75), width = 0.5) +
  scale_y_continuous(labels = scales::percent, limits = c(0, 1), breaks = c(0, 0.25, 0.5, 0.75, 1), expand = c(0,0))+
  scale_fill_manual(name = "Age group (years)",
                    values = c("grey80", "grey60", "grey40", "grey20", "grey10"))+
  labs(y = "Visits (%) with height",
       x = "Hospital",
       title = "Emergency visit")+
  theme_minimal()+
  theme(panel.grid.major.x = element_blank(),
        axis.text = element_text(color = "black", size = 8),
        axis.title = element_text(color = "black", size = 8),
        title = element_text(color = "black", size = 8, face = "bold"))

plot_height_by_hospital_coded_ER

plot_height_by_hospital_coded_inpatient <- plot_data |> 
  filter(visit_week_type == "Inpatient stay") |> 
  ggplot(aes(x = hospital_coded, y = yes_prop, fill = age_group)) + 
  geom_col(stat = "identity", position = position_dodge(width = 0.75), width = 0.75)+
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = 0.75), width = 0.5) +
  scale_y_continuous(labels = scales::percent, limits = c(0, 1), breaks = c(0, 0.25, 0.5, 0.75, 1), expand = c(0,0))+
  scale_fill_manual(name = "Age group (years)",
                    values = c("grey80", "grey60", "grey40", "grey20", "grey10"))+
  labs(y = "Visits (%) with height",
       x = "Hospital",
       title = "Inpatient stay")+
  theme_minimal()+
  theme(panel.grid.major.x = element_blank(),
        axis.text = element_text(color = "black", size = 8),
        axis.title = element_text(color = "black", size = 8),
        title = element_text(color = "black", size = 8, face = "bold"))

plot_height_by_hospital_coded_inpatient




```


Weight

```{r}

plot_data <- data_visit_week |>
  mutate(weight_measurement = case_when(number_weight_measurements >= 1 ~ "yes",
                                                TRUE ~ "no")) |>
  select(hospital_coded, weight_measurement, visit_week_type, age_group) |>
  group_by(hospital_coded, visit_week_type, age_group) |>
  count(weight_measurement) |>
  ungroup() |>
  pivot_wider(names_from = weight_measurement,
              values_from = n,
              values_fill = 0) |>
  mutate(total = yes + no,
         yes_prop = yes / total) |>
  rowwise() |>
  mutate(
    ci = list(prop.test(yes, total)$conf.int),
    ci_lower = ci[1],
    ci_upper = ci[2]
  ) |>
  ungroup() |>
  select(-ci)

plot_weight_by_hospital_coded_outpatient <- plot_data |> 
  filter(visit_week_type == "Outpatient visit") |> 
  ggplot(aes(x = hospital_coded, y = yes_prop, fill = age_group)) + 
  geom_col(stat = "identity", position = position_dodge(width = 0.75), width = 0.75)+
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = 0.75), width = 0.5) +
  scale_y_continuous(labels = scales::percent, limits = c(0, 1), breaks = c(0, 0.25, 0.5, 0.75, 1), expand = c(0,0))+
  scale_fill_manual(values = c("grey80", "grey60", "grey40", "grey20", "grey10"))+
  labs(y = "Visits (%) with weight",
       x = "Hospital",
       title = "Outpatient visit",
       fill = "Age group (years)")+
  theme_minimal()+
  theme(panel.grid.major.x = element_blank(),
        axis.text = element_text(color = "black", size = 8),
        axis.title = element_text(color = "black", size = 8),
        title = element_text(color = "black", size = 8, face = "bold"))

plot_weight_by_hospital_coded_outpatient

plot_weight_by_hospital_coded_ER <- plot_data |> 
  filter(visit_week_type == "ER visit") |> 
  ggplot(aes(x = hospital_coded, y = yes_prop, fill = age_group)) + 
  geom_col(stat = "identity", position = position_dodge(width = 0.75), width = 0.75)+
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = 0.75), width = 0.5) +
  scale_y_continuous(labels = scales::percent, limits = c(0, 1), breaks = c(0, 0.25, 0.5, 0.75, 1), expand = c(0,0))+
  scale_fill_manual(values = c("grey80", "grey60", "grey40", "grey20", "grey10"))+
  labs(y = "Visits (%) with weight",
       x = "Hospital",
       title = "Emergency visit",
       fill = "Age group (years)")+
  theme_minimal()+
  theme(panel.grid.major.x = element_blank(),
        axis.text = element_text(color = "black", size = 8),
        axis.title = element_text(color = "black", size = 8),
        title = element_text(color = "black", size = 8, face = "bold"))

plot_weight_by_hospital_coded_ER

plot_weight_by_hospital_coded_inpatient <- plot_data |> 
  filter(visit_week_type == "Inpatient stay") |> 
  ggplot(aes(x = hospital_coded, y = yes_prop, fill = age_group)) + 
  geom_col(stat = "identity", position = position_dodge(width = 0.75), width = 0.75)+
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = 0.75), width = 0.5) +
  scale_y_continuous(labels = scales::percent, limits = c(0, 1), breaks = c(0, 0.25, 0.5, 0.75, 1), expand = c(0,0))+
  scale_fill_manual(values = c("grey80", "grey60", "grey40", "grey20", "grey10"))+
  labs(y = "Stays (%) with weight",
       x = "Hospital",
       title = "Inpatient stay",
       fill = "Age group (years)")+
  theme_minimal()+
  theme(panel.grid.major.x = element_blank(),
        axis.text = element_text(color = "black", size = 8),
        axis.title = element_text(color = "black", size = 8),
        title = element_text(color = "black", size = 8, face = "bold"),
        legend.position = "bottom",
        legend.key.height = unit(0.5, "cm"),
        legend.key.width = unit(0.25, "cm"))

plot_weight_by_hospital_coded_inpatient

```


Combined

```{r}

plot_height_availability_per_visit_by_hospital_coded <- plot_grid(plotlist = c(plot_height_by_hospital_coded_outpatient + theme(legend.position = "None"),
                                                                    plot_height_by_hospital_coded_ER + theme(legend.position = "None"),
                                                                    plot_height_by_hospital_coded_inpatient + theme(legend.position = "None")),
                                                       ncol = 1)

plot_weight_availability_per_visit_by_hospital_coded <- plot_grid(plotlist = c(plot_weight_by_hospital_coded_outpatient + theme(legend.position = "None"),
                                                                    plot_weight_by_hospital_coded_ER + theme(legend.position = "None"),
                                                                    plot_weight_by_hospital_coded_inpatient + theme(legend.position = "None")),
                                                       ncol = 1)

plot_availability_per_visit_by_hospital_coded <- plot_grid(plotlist = c(plot_height_availability_per_visit_by_hospital_coded + theme(plot.margin = margin(t = 1, r = 0, b = 0, l = 0, unit = "cm")),
                                                                    plot_weight_availability_per_visit_by_hospital_coded+ theme(plot.margin = margin(t = 1, r = 0, b = 0, l = 0, unit = "cm"))),
                                                       ncol = 2,
                                                       labels = c("Height", "Weight"),
                                                       label_x = 0.5,
                                                       hjust = 0.5)

plot_availability_per_visit_by_hospital_coded

get_legend2 <- function(a.gplot){
  if (!gtable::is.gtable(a.gplot))
    a.gplot <- ggplotGrob(a.gplot)
  leg <- which(sapply(a.gplot$grobs, function(x) x$name) == "guide-box")
  a.gplot$grobs[[leg]]
}

plot_legend <- get_legend2(plot_weight_by_hospital_coded_inpatient + theme(legend.position = "bottom",
                                                                           legend.title.position ="top",
                                                                           legend.title = element_text(hjust = 0.5)))

plot_availability_per_visit_by_hospital_coded_with_legend <- plot_grid(plotlist = list(plot_availability_per_visit_by_hospital_coded,
                                                                              plot_legend),
                                                                 ncol = 1,
                                                                 rel_heights = c(1, 0.1))

plot_availability_per_visit_by_hospital_coded_with_legend

ggsave(plot_availability_per_visit_by_hospital_coded_with_legend, filename = here("output", "figures", "plot_availability_per_visit_by_hospital_coded_with_legend.svg"), width = 18, height = 22, units = "cm")


```


#### eFigure: HC and BMI by hospital_coded, visity type, age group

HC

```{r}

plot_data <- data_visit_week |>
  mutate(head_measurement = case_when(number_head_measurements >= 1 ~ "yes",
                                                TRUE ~ "no")) |>
  select(hospital_coded, head_measurement, visit_week_type, age_group) |>
  group_by(hospital_coded, visit_week_type, age_group) |>
  count(head_measurement) |>
  ungroup() |>
  pivot_wider(names_from = head_measurement,
              values_from = n,
              values_fill = 0) |>
  mutate(total = yes + no,
         yes_prop = yes / total) |>
  rowwise() |>
  mutate(
    ci = list(prop.test(yes, total)$conf.int),
    ci_lower = ci[1],
    ci_upper = ci[2]
  ) |>
  ungroup() |>
  select(-ci)

plot_head_by_hospital_coded_outpatient <- plot_data |> 
  filter(visit_week_type == "Outpatient visit") |> 
  ggplot(aes(x = hospital_coded, y = yes_prop, fill = age_group)) + 
  geom_col(stat = "identity", position = position_dodge(width = 0.75), width = 0.75)+
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = 0.75), width = 0.5) +
  scale_y_continuous(labels = scales::percent, limits = c(0, 1), breaks = c(0, 0.25, 0.5, 0.75, 1), expand = c(0,0))+
  scale_fill_manual(values = c("grey80", "grey60", "grey40", "grey20", "grey10"))+
  labs(y = "Visits (%) with HC",
       x = "Hospital",
       title = "Outpatient visit",
       fill = "Age group (years)")+
  theme_minimal()+
  theme(panel.grid.major.x = element_blank(),
        axis.text = element_text(color = "black", size = 8),
        axis.title = element_text(color = "black", size = 8),
        title = element_text(color = "black", size = 8, face = "bold"))

plot_head_by_hospital_coded_outpatient

plot_head_by_hospital_coded_ER <- plot_data |> 
  filter(visit_week_type == "ER visit") |> 
  ggplot(aes(x = hospital_coded, y = yes_prop, fill = age_group)) + 
  geom_col(stat = "identity", position = position_dodge(width = 0.75), width = 0.75)+
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = 0.75), width = 0.5) +
  scale_y_continuous(labels = scales::percent, limits = c(0, 1), breaks = c(0, 0.25, 0.5, 0.75, 1), expand = c(0,0))+
  scale_fill_manual(values = c("grey80", "grey60", "grey40", "grey20", "grey10"))+
  labs(y = "Visits (%) with HC",
       x = "Hospital",
       title = "Emergency visit",
       fill = "Age group (years)")+
  theme_minimal()+
  theme(panel.grid.major.x = element_blank(),
        axis.text = element_text(color = "black", size = 8),
        axis.title = element_text(color = "black", size = 8),
        title = element_text(color = "black", size = 8, face = "bold"))

plot_head_by_hospital_coded_ER

plot_head_by_hospital_coded_inpatient <- plot_data |> 
  filter(visit_week_type == "Inpatient stay") |> 
  ggplot(aes(x = hospital_coded, y = yes_prop, fill = age_group)) + 
  geom_col(stat = "identity", position = position_dodge(width = 0.75), width = 0.75)+
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = 0.75), width = 0.5) +
  scale_y_continuous(labels = scales::percent, limits = c(0, 1), breaks = c(0, 0.25, 0.5, 0.75, 1), expand = c(0,0))+
  scale_fill_manual(values = c("grey80", "grey60", "grey40", "grey20", "grey10"))+
  labs(y = "Stays (%) with HC",
       x = "Hospital",
       title = "Inpatient stay",
       fill = "Age group (years)")+
  theme_minimal()+
  theme(panel.grid.major.x = element_blank(),
        axis.text = element_text(color = "black", size = 8),
        axis.title = element_text(color = "black", size = 8),
        title = element_text(color = "black", size = 8, face = "bold"))

plot_head_by_hospital_coded_inpatient




```


BMI

```{r}

plot_data <- data_visit_week |>
  mutate(bmi_measurement = case_when(number_bmi_measurements >= 1 ~ "yes",
                                                TRUE ~ "no")) |>
  select(hospital_coded, bmi_measurement, visit_week_type, age_group) |>
  group_by(hospital_coded, visit_week_type, age_group) |>
  count(bmi_measurement) |>
  ungroup() |>
  pivot_wider(names_from = bmi_measurement,
              values_from = n,
              values_fill = 0) |>
  mutate(total = yes + no,
         yes_prop = yes / total) |>
  rowwise() |>
  mutate(
    ci = list(prop.test(yes, total)$conf.int),
    ci_lower = ci[1],
    ci_upper = ci[2]
  ) |>
  ungroup() |>
  select(-ci)

plot_bmi_by_hospital_coded_outpatient <- plot_data |> 
  filter(visit_week_type == "Outpatient visit") |> 
  ggplot(aes(x = hospital_coded, y = yes_prop, fill = age_group)) + 
  geom_col(stat = "identity", position = position_dodge(width = 0.75), width = 0.75)+
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = 0.75), width = 0.5) +
  scale_y_continuous(labels = scales::percent, limits = c(0, 1), breaks = c(0, 0.25, 0.5, 0.75, 1), expand = c(0,0))+
  scale_fill_manual(values = c("grey80", "grey60", "grey40", "grey20", "grey10"))+
  labs(y = "Visits (%) with BMI",
       x = "Hospital",
       title = "Outpatient visit",
       fill = "Age group (years)")+
  theme_minimal()+
  theme(panel.grid.major.x = element_blank(),
        axis.text = element_text(color = "black", size = 8),
        axis.title = element_text(color = "black", size = 8),
        title = element_text(color = "black", size = 8, face = "bold"))

plot_bmi_by_hospital_coded_outpatient

plot_bmi_by_hospital_coded_ER <- plot_data |> 
  filter(visit_week_type == "ER visit") |> 
  ggplot(aes(x = hospital_coded, y = yes_prop, fill = age_group)) + 
  geom_col(stat = "identity", position = position_dodge(width = 0.75), width = 0.75)+
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = 0.75), width = 0.5) +
  scale_y_continuous(labels = scales::percent, limits = c(0, 1), breaks = c(0, 0.25, 0.5, 0.75, 1), expand = c(0,0))+
  scale_fill_manual(values = c("grey80", "grey60", "grey40", "grey20", "grey10"))+
  labs(y = "Visits (%) with BMI",
       x = "Hospital",
       title = "Emergency visit",
       fill = "Age group (years)")+
  theme_minimal()+
  theme(panel.grid.major.x = element_blank(),
        axis.text = element_text(color = "black", size = 8),
        axis.title = element_text(color = "black", size = 8),
        title = element_text(color = "black", size = 8, face = "bold"))

plot_bmi_by_hospital_coded_ER

plot_bmi_by_hospital_coded_inpatient <- plot_data |> 
  filter(visit_week_type == "Inpatient stay") |> 
  ggplot(aes(x = hospital_coded, y = yes_prop, fill = age_group)) + 
  geom_col(stat = "identity", position = position_dodge(width = 0.75), width = 0.75)+
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = 0.75), width = 0.5) +
  scale_y_continuous(labels = scales::percent, limits = c(0, 1), breaks = c(0, 0.25, 0.5, 0.75, 1), expand = c(0,0))+
  scale_fill_manual(values = c("grey80", "grey60", "grey40", "grey20", "grey10"))+
  labs(y = "Stays (%) with BMI",
       x = "Hospital",
       title = "Inpatient stay",
       fill = "Age group (years)")+
  theme_minimal()+
  theme(panel.grid.major.x = element_blank(),
        axis.text = element_text(color = "black", size = 8),
        axis.title = element_text(color = "black", size = 8),
        title = element_text(color = "black", size = 8, face = "bold"),
        legend.position = "bottom",
        legend.key.height = unit(0.5, "cm"),
        legend.key.width = unit(0.25, "cm"))

plot_bmi_by_hospital_coded_inpatient

```


Combined

```{r}

plot_head_availability_per_visit_by_hospital_coded <- plot_grid(plotlist = c(plot_head_by_hospital_coded_outpatient + theme(legend.position = "None"),
                                                                    plot_head_by_hospital_coded_ER + theme(legend.position = "None"),
                                                                    plot_head_by_hospital_coded_inpatient + theme(legend.position = "None")),
                                                       ncol = 1)

plot_bmi_availability_per_visit_by_hospital_coded <- plot_grid(plotlist = c(plot_bmi_by_hospital_coded_outpatient + theme(legend.position = "None"),
                                                                    plot_bmi_by_hospital_coded_ER + theme(legend.position = "None"),
                                                                    plot_bmi_by_hospital_coded_inpatient + theme(legend.position = "None")),
                                                       ncol = 1)

plot_HC_bmi_availability_per_visit_by_hospital_coded <- plot_grid(plotlist = c(plot_head_availability_per_visit_by_hospital_coded + theme(plot.margin = margin(t = 1, r = 0, b = 0, l = 0, unit = "cm")),
                                                                    plot_bmi_availability_per_visit_by_hospital_coded+ theme(plot.margin = margin(t = 1, r = 0, b = 0, l = 0, unit = "cm"))),
                                                       ncol = 2,
                                                       labels = c("Head circumference", "Body mass index"),
                                                       label_x = 0.5,
                                                       hjust = 0.5)

plot_HC_bmi_availability_per_visit_by_hospital_coded

get_legend2 <- function(a.gplot){
  if (!gtable::is.gtable(a.gplot))
    a.gplot <- ggplotGrob(a.gplot)
  leg <- which(sapply(a.gplot$grobs, function(x) x$name) == "guide-box")
  a.gplot$grobs[[leg]]
}

plot_legend <- get_legend2(plot_bmi_by_hospital_coded_inpatient + theme(legend.position = "bottom",
                                                                           legend.title.position ="top",
                                                                           legend.title = element_text(hjust = 0.5)))

plot_HC_bmi_availability_per_visit_by_hospital_coded_with_legend <- plot_grid(plotlist = list(plot_HC_bmi_availability_per_visit_by_hospital_coded,
                                                                              plot_legend),
                                                                 ncol = 1,
                                                                 rel_heights = c(1, 0.1))

plot_HC_bmi_availability_per_visit_by_hospital_coded_with_legend

ggsave(plot_HC_bmi_availability_per_visit_by_hospital_coded_with_legend, filename = here("output", "figures", "plot_HC_bmi_availability_per_visit_by_hospital_coded_with_legend.svg"), width = 18, height = 22, units = "cm")


```


## Aim 2: Quality


### eTable : Growthclenr output

```{r}

data_height_original |> 
  select(gcr_result) |> 
  tbl_summary(statistic = all_categorical() ~ "{n} ({p})",
              missing = "ifany",
              missing_stat = "{N_miss} ({p_miss})",
              label = list(result = "Quality of heights"),
              digits = everything() ~ 0)


data_weight_original |> 
  select(gcr_result) |> 
  tbl_summary(statistic = all_categorical() ~ "{n} ({p})",
              missing = "ifany",
              missing_stat = "{N_miss} ({p_miss})",
              label = list(result = "Quality of weights"),
              digits = everything() ~ 0)

```

### eTable: manual result

```{r}

data_height_original |> 
  select(manual_result_fct) |> 
  tbl_summary(statistic = all_categorical() ~ "{n} ({p})",
              missing = "ifany",
              missing_stat = "{N_miss} ({p_miss})",
              label = list(result = "Quality of heights"),
              digits = everything() ~ 0)


data_weight_original |> 
  select(manual_result_fct) |> 
  tbl_summary(statistic = all_categorical() ~ "{n} ({p})",
              missing = "ifany",
              missing_stat = "{N_miss} ({p_miss})",
              label = list(result = "Quality of weights"),
              digits = everything() ~ 0)

```


### eTable: Quality

```{r}

data_height_original |> 
  select(combined_result_fct) |> 
  tbl_summary(statistic = all_categorical() ~ "{n} ({p})",
              missing = "ifany",
              missing_stat = "{N_miss} ({p_miss})",
              label = list(result = "Quality of heights"),
              digits = everything() ~ 0)


data_weight_original |> 
  select(combined_result_fct) |> 
  tbl_summary(statistic = all_categorical() ~ "{n} ({p})",
              missing = "ifany",
              missing_stat = "{N_miss} ({p_miss})",
              label = list(result = "Quality of weights"),
              digits = everything() ~ 0)


data_head |> 
  select(manual_result_fct) |> 
  tbl_summary(statistic = all_categorical() ~ "{n} ({p})",
              missing = "ifany",
              missing_stat = "{N_miss} ({p_miss})",
              label = list(result = "Quality of weights"),
              digits = everything() ~ 0)


data_bmi |> 
  select(combined_result_fct) |> 
  tbl_summary(statistic = all_categorical() ~ "{n} ({p})",
              missing = "ifany",
              missing_stat = "{N_miss} ({p_miss})",
              label = list(result = "Quality of weights"),
              digits = everything() ~ 0)

```



### Figure 1: Sankey-plot of height and weight quality


```{r}

data_sankey_height <- data_height_original |> 
  mutate(manual_result_fct = factor(case_when(
    manual_result_fct == "Include - No error" ~ "No error",
    manual_result_fct == "Include - Swapped-Recoding-Include-as-Weight" ~ "Corrected error",
    manual_result_fct == "Include - Corrected unit error" ~ "Corrected error",
    manual_result_fct == "Include - Corrected decimal point error" ~ "Corrected error",
    manual_result_fct == "Duplicate - Carried forward" ~ "Duplicate",
    manual_result_fct == "Duplicate - Same day" ~ "Duplicate",
    manual_result_fct == "Exclude - Z-score" ~ "Biologically implausible outlier",
    manual_result_fct == "Missing - Negative age" ~ "Invalid",
    manual_result_fct == "Missing - Zero or negative recording" ~ "Invalid"),
    levels = c("Invalid", "Biologically implausible outlier", "Duplicate", "Corrected error", "No error"))) %>%
  mutate(growthcleanr_result_fct = factor(case_when(
    growthcleanr_result_fct == "Include - No error" ~ "No error",
    growthcleanr_result_fct == "Include - Corrected swapped measurements" ~ "Corrected error",
    growthcleanr_result_fct == "Duplicate - Carried forward" ~ "Duplicate",
    growthcleanr_result_fct == "Duplicate - Same day" ~ "Duplicate",
    growthcleanr_result_fct == "Exclude - Single outlier" ~ "Biologically implausible outlier",
    growthcleanr_result_fct == "Exclude - Longitudinal outlier" ~ "Biologically implausible outlier",
    growthcleanr_result_fct == "Missing" ~ "Invalid"
  ), levels = c("Invalid", "Biologically implausible outlier", "Duplicate", "Corrected error", "No error"))) %>%
  mutate(combined_result_fct = factor(case_when(
    combined_result_fct == "Include - No-Error" ~ "No error",
    combined_result_fct == "Include - Swapped-Recoding-Include-as-Weight" ~ "Corrected error",
    combined_result_fct == "Include - Corrected-Unit-Error" ~ "Corrected error",
    combined_result_fct == "Include - Corrected-Decimal-Error" ~ "Corrected error",
    combined_result_fct == "Carried-Forward" ~ "Duplicate",
    combined_result_fct == "Same-Day" ~ "Duplicate",
    combined_result_fct == "Exclude - Single-Outlier" ~ "Biologically implausible outlier",
    combined_result_fct == "Exclude - Longitudinal-Outlier" ~ "Biologically implausible outlier",
    combined_result_fct == "Exclude - Z-Score" ~ "Biologically implausible outlier",
    combined_result_fct == "Missing - Age" ~ "Invalid",
    combined_result_fct == "Missing - Recording" ~ "Invalid"
  ), levels = c("Invalid", "Biologically implausible outlier", "Duplicate", "Corrected error", "No error"))) |> 
  select(height_id, manual_result_fct, growthcleanr_result_fct, combined_result_fct) |> 
  count(manual_result_fct, growthcleanr_result_fct, combined_result_fct)

data_sankey_height <- data_sankey_height |> 
  pivot_stages_longer(stages_from = c("manual_result_fct",  "combined_result_fct", "growthcleanr_result_fct"),
                      values_from = "n") |> 
  mutate(node = factor(node, levels = c("Invalid", "Biologically implausible outlier", "Duplicate", "Corrected error", "No error")),
         stage = factor(stage, levels = c("manual_result_fct",  "combined_result_fct", "growthcleanr_result_fct"),
                        labels = c("Own algorithm", "Combined", "Growthcleanr")))

v_space = round(data_height_original |> nrow()/12)

pos <- position_sankey(split_nodes = FALSE, align = "top",
                       width = 0.6, v_space = v_space, order = "as_is")

node_labels <- data_sankey_height %>%
  filter((stage == "Own algorithm" & connector == "from") | (stage == "Combined" & connector == "from") | (stage == "Growthcleanr" & connector == "to")) |> 
  group_by(stage, node) %>%
  summarize(n = sum(n), .groups = "drop") %>%
  ungroup() |>  
  group_by(stage) |> 
  arrange(node) |> 
  mutate(sum = sum(n),
         prop = n/sum,
         label = paste0(format(n, big.mark = ",", scientific = FALSE), " (", ifelse(round(prop*100)>=1, round(prop*100), "<1"), "%)"),
         y = cumsum(n) + v_space * (4-(n()-row_number())) - n/2)

data_sankey_height <- data_sankey_height |> 
  left_join(node_labels |> select(stage, node, y, label), by = c("stage", "node"))

data_sankey_height <- data_sankey_height %>%
  mutate(
    edge_color = case_when(
      stage == "Combined" & connector == "to"  ~ node,      # coming from left → use left node
      stage == "Combined" & connector == "from" ~ node,     # going to right → use right node
      connector == "from" ~ node,
      TRUE ~ node
    )
  ) %>%
  group_by(edge_id) %>%
  mutate(
    edge_color = case_when(
      stage == "Combined" & connector == "to"   ~ node[connector == "from"], # from left
      stage == "Combined" & connector == "from" ~ node[connector == "to"],   # from right
      connector == "from" ~ node,
      TRUE ~ node
    )
  ) %>%
  ungroup()



plot_sankey_height <- data_sankey_height |> 
  ggplot(aes(x = stage, y = n, group = node, connector = connector, edge_id = edge_id)) +
  geom_sankeyedge(position = pos, aes(fill = edge_color, color = edge_color)) +
  geom_sankeynode(position = pos, aes(fill = node, color = node)) +
  geom_label(aes(x = stage, y = y, label = label),
            fill="white", color = "black", size = 3.5) +
  scale_x_discrete(position = "top", expand = c(0, 0), labels = c("Self-developed\nalgorithm", "Combined\nalgorithms", "Growthcleanr\nalgorithm")) +
  scale_fill_manual(name = "Result",
                    values = c(
    "No error" = "#0080a4",
    "Corrected error" = "#36b5b6",
    "Duplicate" = "#c2b600",
    "Biologically implausible outlier" = "#e6002e",
    "Invalid" = "black"
  )) +
  scale_colour_manual(values = c(
    "No error" = "#0080a4",
    "Corrected error" = "#36b5b6",
    "Duplicate" = "#c2b600",
    "Biologically implausible outlier" = "#e6002e",
    "Invalid" = "black"
  ), guide = "none") +
  theme_void()+
  theme(
    axis.text.x = element_text(size = 11, margin = margin(b = 0)),
    legend.position = "None",
    plot.margin = unit(c(b = 1, t = 1, r = 0.5, l = 0.5), "cm")
  )

plot_sankey_height

```

```{r}

data_sankey_weight <- data_weight_original |> 
  mutate(manual_result_fct = factor(case_when(
    manual_result_fct == "Include - No error" ~ "No error",
    manual_result_fct == "Include - Swapped-Recoding-Include-as-Height" ~ "Corrected error",
    manual_result_fct == "Include - Corrected unit error" ~ "Corrected error",
    manual_result_fct == "Include - Corrected decimal point error" ~ "Corrected error",
    manual_result_fct == "Duplicate - Carried forward" ~ "Duplicate",
    manual_result_fct == "Duplicate - Same day" ~ "Duplicate",
    manual_result_fct == "Exclude - Z-score" ~ "Biologically implausible outlier",
    manual_result_fct == "Missing - Negative age" ~ "Invalid",
    manual_result_fct == "Missing - Zero or negative recording" ~ "Invalid"),
    levels = c("Invalid", "Biologically implausible outlier", "Duplicate", "Corrected error", "No error"))) %>%
  mutate(growthcleanr_result_fct = factor(case_when(
    growthcleanr_result_fct == "Include - No error" ~ "No error",
    growthcleanr_result_fct == "Include - Corrected swapped measurements" ~ "Corrected error",
    growthcleanr_result_fct == "Duplicate - Carried forward" ~ "Duplicate",
    growthcleanr_result_fct == "Duplicate - Same day" ~ "Duplicate",
    growthcleanr_result_fct == "Exclude - Single outlier" ~ "Biologically implausible outlier",
    growthcleanr_result_fct == "Exclude - Longitudinal outlier" ~ "Biologically implausible outlier",
    growthcleanr_result_fct == "Missing" ~ "Invalid"
  ), levels = c("Invalid", "Biologically implausible outlier", "Duplicate", "Corrected error", "No error"))) %>%
  mutate(combined_result_fct = factor(case_when(
    combined_result_fct == "Include - No-Error" ~ "No error",
    combined_result_fct == "Include - Corrected-Unit-Error" ~ "Corrected error",
    combined_result_fct == "Include - Corrected-Decimal-Error" ~ "Corrected error",
    combined_result_fct == "Include - Swapped-Recoding-Include-as-Height" ~ "Corrected error",
    combined_result_fct == "Carried-Forward" ~ "Duplicate",
    combined_result_fct == "Same-Day" ~ "Duplicate",
    combined_result_fct == "Exclude - Single-Outlier" ~ "Biologically implausible outlier",
    combined_result_fct == "Exclude - Longitudinal-Outlier" ~ "Biologically implausible outlier",
    combined_result_fct == "Exclude - Z-Score" ~ "Biologically implausible outlier",
    combined_result_fct == "Missing - Age" ~ "Invalid",
    combined_result_fct == "Missing - Recording" ~ "Invalid"
  ), levels = c("Invalid", "Biologically implausible outlier", "Duplicate", "Corrected error", "No error"))) |> 
  select(weight_id, manual_result_fct, growthcleanr_result_fct, combined_result_fct) |> 
  count(manual_result_fct, growthcleanr_result_fct, combined_result_fct)

data_sankey_weight <- data_sankey_weight |> 
  pivot_stages_longer(stages_from = c("manual_result_fct",  "combined_result_fct", "growthcleanr_result_fct"),
                      values_from = "n") |> 
  mutate(node = factor(node, levels = c("Invalid", "Biologically implausible outlier", "Duplicate", "Corrected error", "No error")),
         stage = factor(stage, levels = c("manual_result_fct",  "combined_result_fct", "growthcleanr_result_fct"),
                        labels = c("Own algorithm", "Combined", "Growthcleanr")))

v_space = round(data_weight_original |> nrow()/12)

pos <- position_sankey(split_nodes = FALSE, align = "top",
                       width = 0.6, v_space = v_space, order = "as_is")

node_labels <- data_sankey_weight %>%
  filter((stage == "Own algorithm" & connector == "from") | (stage == "Combined" & connector == "from") | (stage == "Growthcleanr" & connector == "to")) |> 
  group_by(stage, node) %>%
  summarize(n = sum(n), .groups = "drop") %>%
  ungroup() |>  
  group_by(stage) |> 
  arrange(node) |> 
  mutate(sum = sum(n),
         prop = n/sum,
         label = paste0(format(n, big.mark = ",", scientific = FALSE), " (", ifelse(round(prop*100)>=1, round(prop*100), "<1"), "%)"),
         y = cumsum(n) + v_space * (4-(n()-row_number())) - n/2)

data_sankey_weight <- data_sankey_weight |> 
  left_join(node_labels |> select(stage, node, y, label), by = c("stage", "node"))

data_sankey_weight <- data_sankey_weight %>%
  mutate(
    edge_color = case_when(
      stage == "Combined" & connector == "to"  ~ node,      # coming from left → use left node
      stage == "Combined" & connector == "from" ~ node,     # going to right → use right node
      connector == "from" ~ node,
      TRUE ~ node
    )
  ) %>%
  group_by(edge_id) %>%
  mutate(
    edge_color = case_when(
      stage == "Combined" & connector == "to"   ~ node[connector == "from"], # from left
      stage == "Combined" & connector == "from" ~ node[connector == "to"],   # from right
      connector == "from" ~ node,
      TRUE ~ node
    )
  ) %>%
  ungroup()



plot_sankey_weight <- data_sankey_weight |> 
  ggplot(aes(x = stage, y = n, group = node, connector = connector, edge_id = edge_id)) +
  geom_sankeyedge(position = pos, aes(fill = edge_color, color = edge_color)) +
  geom_sankeynode(position = pos, aes(fill = node, color = node)) +
  geom_label(aes(x = stage, y = y, label = label),
            fill="white", color = "black", size = 3.5) +
  scale_x_discrete(position = "top", expand = c(0, 0), labels = c("Self-developed\nalgorithm", "Combined\nalgorithms", "Growthcleanr\nalgorithm")) +
  scale_fill_manual(name = "Result",
                    values = c(
    "No error" = "#0080a4",
    "Corrected error" = "#36b5b6",
    "Duplicate" = "#c2b600",
    "Biologically implausible outlier" = "#e6002e",
    "Invalid" = "black"
  )) +
  scale_colour_manual(values = c(
    "No error" = "#0080a4",
    "Corrected error" = "#36b5b6",
    "Duplicate" = "#c2b600",
    "Biologically implausible outlier" = "#e6002e",
    "Invalid" = "black"
  ), guide = "none") +
  theme_void()+
  theme(
    axis.text.x = element_text(size = 11, margin = margin(b = 0)),
    legend.title = element_text(size = 11),
    legend.text = element_text(size = 11),
    legend.position = "bottom",
    plot.margin = unit(c(b = 1, t = 1, r = 0.5, l = 0.5), "cm")
  )

plot_sankey_weight



plot_legend <- get_legend2(plot_sankey_weight + theme(plot.margin = unit(c(b = 0, t = 0, r = 10, l = 10), "pt"),
                                                      legend.title = element_blank()))

plot_sankey <- plot_grid(plot_sankey_height,
                         plot_sankey_weight + theme(legend.position = "None"),
                         plot_legend,
                         ncol=1,
                         rel_heights = c(1,1,0.1),
                         align = "h",
                         axis = "l",
                         labels = c("Height", "Weight"),
                         label_x = c(-0.02, -0.02))

ggsave(plot_sankey, filename = here("output", "figures", "plot_sankey.svg"), width = 18, height = 22, units = "cm")

```

### Figure 2: Included vs. excluded height, weight, BMI over age

Height

```{r}

plot_height_before_cleaning <- data_height_original |> 
  ggplot(aes(x = age_years_height, y = original_height_cm))+
  geom_point(alpha = 0.2, color = "black", fill = "black")+
  scale_x_continuous(limits = c(0, 20), expand = c(0,0))+
  scale_y_continuous(limits = c(0, 220), expand = c(0,0))+
  ggtitle("Original dataset")+
  xlab("Age (years)")+
  ylab("Height (cm)")+
  theme_minimal()+
  theme(legend.position = "None",
        plot.title = element_text(size = 10, color = "black", face = "bold", hjust = 0.5),
        axis.text = element_text(size=10, color = "black"),
        axis.title = element_text(size=10, color = "black"),
        legend.title = element_blank(),
        legend.text = element_text(size = 10, color = "black"),
        plot.margin = unit(c(b = 0, t = 1, r = 0.5, l = 0.5), "cm"))

plot_height_before_cleaning

plot_height_during_cleaning <- data_height_clean |> 
  mutate(include = case_when(combined_result == "Include - No-Error" ~ "Included",
                             combined_result == "Include - Corrected-Unit-Error" ~ "Included",
                             combined_result == "Include - Corrected-Decimal-Error" ~ "Included",
                             combined_result == "Include - Swapped-Recoding-Include-as-Height" ~ "Included",
                             TRUE ~ "Excluded")) |> 
  ggplot(aes(x = age_years_height, y = height_cm, color = include))+
  geom_point(alpha = 0.2)+
  scale_color_manual(values = c("#e6002e", "#0080a4"))+
  scale_x_continuous(limits = c(0, 20), expand = c(0,0))+
  scale_y_continuous(limits = c(0, 220), expand = c(0,0))+
  labs(color = "Height quality")+
  ggtitle("Data cleaning")+
  xlab("Age (years)")+
  ylab("Height (cm)")+
  theme_minimal()+
  theme(legend.position = "bottom",
        plot.title = element_text(size = 10, color = "black", face = "bold", hjust = 0.5),
        axis.text = element_text(size=10, color = "black"),
        axis.title = element_text(size=10, color = "black"),
        legend.title = element_blank(),
        legend.text = element_text(size = 10, color = "black"),
        plot.margin = unit(c(b = 0, t = 1, r = 0.5, l = 0.5), "cm"))

plot_height_during_cleaning

plot_height_after_cleaning <- data_height_clean |> 
  mutate(include = case_when(combined_result == "Include - No-Error" ~ "Included",
                             combined_result == "Include - Corrected-Unit-Error" ~ "Included",
                             combined_result == "Include - Corrected-Decimal-Error" ~ "Included",
                             combined_result == "Include - Swapped-Recoding-Include-as-Height" ~ "Included",
                             TRUE ~ "Excluded")) |> 
  filter(include == "Included") |> 
  ggplot(aes(x = age_years_height, y = height_cm, color = include))+
  geom_point(alpha = 0.2)+
  scale_color_manual(labels = c("Include"), values = c("#0080a4"))+
  scale_x_continuous(limits = c(0, 20), expand = c(0,0))+
  scale_y_continuous(limits = c(0, 220), expand = c(0,0))+
  labs(color = "Height quality")+
  ggtitle("Cleaned dataset")+
  xlab("Age (years)")+
  ylab("Height (cm)")+
  theme_minimal()+
  theme(legend.position = "bottom",
        plot.title = element_text(size = 10, color = "black", face = "bold", hjust = 0.5),
        axis.text = element_text(size=10, color = "black"),
        axis.title = element_text(size=10, color = "black"),
        legend.title = element_blank(),
        legend.text = element_text(size = 10, color = "black"),
        plot.margin = unit(c(b = 0, t = 1, r = 0.5, l = 0.5), "cm"))

plot_height_quality <- plot_grid(plot_height_before_cleaning + theme(legend.position = "None"),
                                 plot_height_during_cleaning + theme(legend.position = "None"),
                                 plot_height_after_cleaning + theme(legend.position = "None"),
                                 ncol = 3,
                                 align = "hv")

plot_height_quality

```

weight

```{r}

plot_weight_before_cleaning <- data_weight_original |> 
  ggplot(aes(x = age_years_weight, y = original_weight_kg))+
  geom_point(alpha = 0.2, color = "black", fill = "black")+
  scale_x_continuous(limits = c(0, 20), expand = c(0,0))+
  scale_y_continuous(limits = c(0, 250), expand = c(0,0))+
  ggtitle(" ")+
  xlab("Age (years)")+
  ylab("Weight (kg)")+
  theme_minimal()+
  theme(legend.position = "None",
        plot.title = element_text(size = 10, color = "black", face = "bold", hjust = 0.5),
        axis.text = element_text(size=10, color = "black"),
        axis.title = element_text(size=10, color = "black"),
        legend.title = element_blank(),
        legend.text = element_text(size = 10, color = "black"),
        plot.margin = unit(c(b = 0, t = 0, r = 0.5, l = 0.5), "cm"))

plot_weight_during_cleaning <- data_weight_clean |> 
  mutate(include = case_when(combined_result == "Include - No-Error" ~ "Included",
                             combined_result == "Include - Corrected-Unit-Error" ~ "Included",
                             combined_result == "Include - Corrected-Decimal-Error" ~ "Included",
                             combined_result == "Include - Swapped-Recoding-Include-as-Weight" ~ "Included",
                             TRUE ~ "Excluded")) |> 
  ggplot(aes(x = age_years_weight, y = weight_kg, color = include))+
  geom_point(alpha = 0.2)+
  scale_color_manual(values = c("#e6002e", "#0080a4"))+
  scale_x_continuous(limits = c(0, 20), expand = c(0,0))+
  scale_y_continuous(limits = c(0, 250), expand = c(0,0))+
  labs(color = "weight quality")+
  ggtitle(" ")+
  xlab("Age (years)")+
  ylab("Weight (kg)")+
  theme_minimal()+
  theme(legend.position = "bottom",
        plot.title = element_text(size = 10, color = "black", face = "bold", hjust = 0.5),
        axis.text = element_text(size=10, color = "black"),
        axis.title = element_text(size=10, color = "black"),
        legend.title = element_blank(),
        legend.text = element_text(size = 10, color = "black"),
        plot.margin = unit(c(b = 0, t = 0, r = 0.5, l = 0.5), "cm"))

plot_weight_during_cleaning

plot_weight_after_cleaning <- data_weight_clean |> 
  mutate(include = case_when(combined_result == "Include - No-Error" ~ "Included",
                             combined_result == "Include - Corrected-Unit-Error" ~ "Included",
                             combined_result == "Include - Corrected-Decimal-Error" ~ "Included",
                             combined_result == "Include - Swapped-Recoding-Include-as-Weight" ~ "Included",
                             TRUE ~ "Excluded")) |> 
  filter(include == "Included") |> 
  ggplot(aes(x = age_years_weight, y = weight_kg, color = include))+
  geom_point(alpha = 0.2)+
  scale_color_manual(labels = c("Include"), values = c("#0080a4"))+
  scale_x_continuous(limits = c(0, 20), expand = c(0,0))+
  scale_y_continuous(limits = c(0, 250), expand = c(0,0))+
  labs(color = "Weight quality")+
  ggtitle(" ")+
  xlab("Age (years)")+
  ylab("Weight (kg)")+
  theme_minimal()+
  theme(legend.position = "None",
        plot.title = element_text(size = 10, color = "black", face = "bold", hjust = 0.5),
        axis.text = element_text(size=10, color = "black"),
        axis.title = element_text(size=10, color = "black"),
        legend.title = element_blank(),
        legend.text = element_text(size = 10, color = "black"),
        plot.margin = unit(c(b = 0, t = 0, r = 0.5, l = 0.5), "cm"))

plot_weight_quality <- plot_grid(plot_weight_before_cleaning + theme(legend.position = "None"),
                                 plot_weight_during_cleaning + theme(legend.position = "None"),
                                 plot_weight_after_cleaning + theme(legend.position = "None"),
                                 ncol = 3,
                                 align = "hv")

plot_weight_quality

```


```{r}
plot_for_legend <- data_weight_clean |> 
  head(3) |> 
  mutate(color = case_when(row_number() == 1 ~ "Original recording",
                           row_number() == 2 ~ "Excluded recording",
                           row_number() == 3 ~ "Included recording")) |> 
  ggplot(aes(x = age_years_weight, y = weight_kg, color = color))+
  geom_point()+
  scale_color_manual(labels = c("Original recording", "Excluded recording", "Included recording"), values = c("black", "#e6002e", "#0080a4"))+
  scale_x_continuous(limits = c(0, 20), expand = c(0,0))+
  scale_y_continuous(limits = c(0, 250), expand = c(0,0))+
  labs(color = "weight quality")+
  ggtitle(" ")+
  xlab("Age (years)")+
  ylab("Weight (kg)")+
  theme_minimal()+
  theme(legend.position = "right",
        plot.title = element_text(size = 10, color = "black", face = "bold", hjust = 0.5),
        axis.text = element_text(size=10, color = "black"),
        axis.title = element_text(size=10, color = "black"),
        legend.title = element_blank(),
        legend.text = element_text(size = 10, color = "black"),
        plot.margin = unit(c(b = 0, t = 0.5, r = 0.5, l = 0.5), "cm"))


```


```{r}
get_legend2 <- function(a.gplot){
  if (!gtable::is.gtable(a.gplot))
    a.gplot <- ggplotGrob(a.gplot)
  leg <- which(sapply(a.gplot$grobs, function(x) x$name) == "guide-box")
  a.gplot$grobs[[leg]]
}

plot_legend <- get_legend2(plot_for_legend + theme(legend.box.background = element_rect(fill = 'white', colour = 'white'),
                                                   plot.background = element_rect(fill = "white", colour = "white")))

plot_quality_height_weight <- plot_grid(plot_height_before_cleaning + theme(legend.position = "None"),
                                        plot_height_during_cleaning + theme(legend.position = "None"),
                                        plot_height_after_cleaning + theme(legend.position = "None"),
                                        plot_weight_before_cleaning + theme(legend.position = "None"),
                                        plot_weight_during_cleaning + theme(legend.position = "None"),
                                        plot_weight_after_cleaning + theme(legend.position = "None"),
                          ncol = 3,
                          align = "hv")

plot_quality_height_weight_with_legend <- plot_grid(plot_quality_height_weight,
                                                    plot_legend,
                                                    ncol = 2,
                                                    rel_widths = c(1,0.2))


ggsave(plot_quality_height_weight_with_legend, filename = here("output", "figures", "plot_quality_height_weight_with_legend.png"), width = 26, height = 16, units = "cm", dpi = 600, bg = "white")

```


#### eFigure: included vs excluded HC and BMI



Head circumference

```{r}

plot_head_before_cleaning <- data_head |> 
  ggplot(aes(x = age_years_circumference, y = original_head_cm))+
  geom_point(alpha = 0.2, color = "black", fill = "black")+
  scale_x_continuous(limits = c(0, 20), expand = c(0,0))+
  scale_y_continuous(limits = c(0, 65), expand = c(0,0))+
  ggtitle("Original dataset")+
  xlab("Age (years)")+
  ylab("Head circumference (cm)")+
  theme_minimal()+
  theme(legend.position = "None",
        plot.title = element_text(size = 10, color = "black", face = "bold", hjust = 0.5),
        axis.text = element_text(size=10, color = "black"),
        axis.title = element_text(size=10, color = "black"),
        legend.title = element_blank(),
        legend.text = element_text(size = 10, color = "black"),
        plot.margin = unit(c(b = 0, t = 1, r = 0.5, l = 0.5), "cm"))

plot_head_during_cleaning <- data_head |> 
  mutate(include = case_when(manual_result_fct == "Include - No error" ~ "Included",
                             manual_result_fct == "Include - Corrected unit error" ~ "Included",
                             manual_result_fct == "Include - Corrected decimal point error" ~ "Included",
                             TRUE ~ "Excluded")) |> 
  ggplot(aes(x = age_years_circumference, y = head_cm, color = include))+
  geom_point(alpha = 0.2)+
  scale_color_manual(labels = c("Exclude", "Include"), values = c("#e6002e", "#0080a4"))+
  scale_x_continuous(limits = c(0, 20), expand = c(0,0))+
  scale_y_continuous(limits = c(0, 65), expand = c(0,0))+
  ggtitle("Data cleaning")+
  xlab("Age (years)")+
  ylab("Head circumference (cm)")+
  theme_minimal()+
  theme(legend.position = "None",
        plot.title = element_text(size = 10, color = "black", face = "bold", hjust = 0.5),
        axis.text = element_text(size=10, color = "black"),
        axis.title = element_text(size=10, color = "black"),
        legend.title = element_blank(),
        legend.text = element_text(size = 10, color = "black"),
        plot.margin = unit(c(b = 0, t = 1, r = 0.5, l = 0.5), "cm"))

plot_head_after_cleaning <- data_head |> 
  mutate(include = case_when(manual_result_fct == "Include - No error" ~ "Included",
                             manual_result_fct == "Include - Corrected unit error" ~ "Included",
                             manual_result_fct == "Include - Corrected decimal point error" ~ "Included",
                             TRUE ~ "Excluded")) |> 
  filter(include == "Included") |> 
  ggplot(aes(x = age_years_circumference, y = head_cm, color = include))+
  geom_point(alpha = 0.2)+
  scale_color_manual(labels = c("Include"), values = c( "#0080a4"))+
  scale_x_continuous(limits = c(0, 20), expand = c(0,0))+
  scale_y_continuous(limits = c(0, 65), expand = c(0,0))+
  ggtitle("Cleaned dataset")+
  xlab("Age (years)")+
  ylab("Head circumference (cm)")+
  theme_minimal()+
  theme(legend.position = "None",
        plot.title = element_text(size = 10, color = "black", face = "bold", hjust = 0.5),
        axis.text = element_text(size=10, color = "black"),
        axis.title = element_text(size=10, color = "black"),
        legend.title = element_blank(),
        legend.text = element_text(size = 10, color = "black"),
        plot.margin = unit(c(b = 0, t = 1, r = 0.5, l = 0.5), "cm"))

plot_head_quality <- plot_grid(plot_head_before_cleaning + theme(legend.position = "None"),
                               plot_head_during_cleaning + theme(legend.position = "None"),
                               plot_head_after_cleaning + theme(legend.position = "None"),
                                 ncol = 3,
                                 align = "hv")

plot_head_quality

```

BMI

```{r}

plot_bmi_before_cleaning <- data_bmi |>
  ggplot(aes(x = age_years_bmi, y = bmi))+
  geom_point(alpha = 0.2, color = "black", fill = "black")+
  scale_x_continuous(limits = c(0, 20), expand = c(0,0))+
  scale_y_continuous(limits = c(0, 65), expand = c(0,0))+
  labs(y = bquote(Body~mass~index~(kg/m^2)),
       x = "Age (years)")+
  theme_minimal()+
  theme(legend.position = "None",
        plot.title = element_text(size = 10, color = "black", face = "bold", hjust = 0.5),
        axis.text = element_text(size=10, color = "black"),
        axis.title = element_text(size=10, color = "black"),
        legend.title = element_blank(),
        legend.text = element_text(size = 10, color = "black"),
        plot.margin = unit(c(b = 0, t = 1, r = 0.5, l = 0.5), "cm"))

plot_bmi_during_cleaning <- data_bmi |>
  mutate(include = case_when(combined_result_fct == "Include - No-Error" ~ "Included",
                             combined_result_fct == "Include - Corrected-Unit-Error" ~ "Included",
                             combined_result_fct == "Include - Corrected-Decimal-Error" ~ "Included",
                             combined_result_fct == "Include - Corrected-Swapped-Measurements" ~ "Included",
                             TRUE ~ "Excluded")) |> 
  ggplot(aes(x = age_years_bmi, y = bmi, color = include))+
  geom_point(alpha = 0.2)+
  scale_color_manual(labels = c("Excluded", "Included"), values = c("#e6002e", "#0080a4"))+
  scale_x_continuous(limits = c(0, 20), expand = c(0,0))+
  scale_y_continuous(limits = c(0, 65), expand = c(0,0))+
  labs(y = bquote(Body~mass~index~(kg/m^2)),
       x = "Age (years)")+
  theme_minimal()+
  theme(legend.position = "None",
        plot.title = element_text(size = 10, color = "black", face = "bold", hjust = 0.5),
        axis.text = element_text(size=10, color = "black"),
        axis.title = element_text(size=10, color = "black"),
        legend.title = element_blank(),
        legend.text = element_text(size = 10, color = "black"),
        plot.margin = unit(c(b = 0, t = 1, r = 0.5, l = 0.5), "cm"))

plot_bmi_after_cleaning <- data_bmi |> 
  mutate(include = case_when(combined_result_fct == "Include - No-Error" ~ "Included",
                             combined_result_fct == "Include - Corrected-Unit-Error" ~ "Included",
                             combined_result_fct == "Include - Corrected-Decimal-Error" ~ "Included",
                             combined_result_fct == "Include - Corrected-Swapped-Measurements" ~ "Included",
                             TRUE ~ "Excluded")) |> 
  filter(include == "Included") |> 
  ggplot(aes(x = age_years_bmi, y = bmi, color = include))+
  geom_point(alpha = 0.2)+
  scale_color_manual(labels = c("Included"), values = c( "#0080a4"))+
  scale_x_continuous(limits = c(0, 20), expand = c(0,0))+
  scale_y_continuous(limits = c(0, 65), expand = c(0,0))+
  labs(y = bquote(Body~mass~index~(kg/m^2)),
       x = "Age (years)")+
  theme_minimal()+
  theme(legend.position = "None",
        plot.title = element_text(size = 10, color = "black", face = "bold", hjust = 0.5),
        axis.text = element_text(size=10, color = "black"),
        axis.title = element_text(size=10, color = "black"),
        legend.title = element_blank(),
        legend.text = element_text(size = 10, color = "black"),
        plot.margin = unit(c(b = 0, t = 1, r = 0.5, l = 0.5), "cm"))

plot_bmi_quality <- plot_grid(plot_bmi_before_cleaning + theme(legend.position = "None"),
                              plot_bmi_during_cleaning + theme(legend.position = "None"),
                              plot_bmi_after_cleaning + theme(legend.position = "None"),
                              ncol = 3,
                              align = "hv")

plot_bmi_quality

```

Combined plots

```{r}

plot_quality_HC_bmi <- plot_grid(plot_head_before_cleaning + theme(legend.position = "None"),
                                        plot_head_during_cleaning + theme(legend.position = "None"),
                                        plot_head_after_cleaning + theme(legend.position = "None"),
                                        plot_bmi_before_cleaning + theme(legend.position = "None"),
                                        plot_bmi_during_cleaning + theme(legend.position = "None"),
                                        plot_bmi_after_cleaning + theme(legend.position = "None"),
                          ncol = 3,
                          align = "hv")

plot_quality_HC_bmi_with_legend <- plot_grid(plot_quality_HC_bmi,
                                                    plot_legend,
                                                    ncol = 2,
                                                    rel_widths = c(1,0.2))


ggsave(plot_quality_HC_bmi_with_legend, filename = here("output", "figures", "plot_quality_HC_bmi_with_legend.png"), width = 26, height = 16, units = "cm", dpi = 600, bg = "white")


```


